---
title: "modelling-with-statcan-workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{modelling-with-statcan-workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>",
  out.width = "100%",
  fig.width = 7,
  fig.height = 5,
  dev = "png",
  dpi = 600
)
```

```{r setup, message=FALSE}
library(osem)
library(dplyr)
library(statcanR)
library(ggplot2)
```
This is a vignette to describe the process of how to run the model, create forecasts, and create hindcasts using data from Statistics Canada via the implemented statcan dictionary within osem.

## Specification

We use a specification for illustrative purposes only. Our specification
contains the following four modules/equations:

```{r specification}
specification <- dplyr::tibble(
    type = c(
      "d",
      "n"
    ),
    dependent = c(
      "EmiCO2Industry",
      "IndProd"
    ),
    independent = c(
      "HICP_GAS + HICP_Energy + IndProd",
      "GAS"

    )
  )
print(specification)
```

## Load statcan dictionary

```{r dictionary}
statcan_dict <- osem::dict_statcan
```

The statcan dictionary contains a different set of variables than found within eurostat. Due to the way Statistics Canada's R package pulls data we need to include all the same headers found within the eurostat dictionary in the statcan dictionary to help with data consistency.

```{r dictionary pt.2}
print(colnames(statcan_dict))
print(colnames(osem::dict))
```

From the default dictionary, we use the EDGAR variable "EmiCO2Industry" and reset the country in the column `geo` to `CA` and then add it to the statcan dictionary:

```{r}
osem::dict %>% 
  dplyr::filter(model_varname == "EmiCO2Industry") %>% 
  dplyr::mutate(geo = "CA") %>% 
  dplyr::bind_rows(statcan_dict,.) -> statcan_dict_ready
```


## Perform modelling
Now let's model the equations we have specified and perform some forecasting.

```{r, mode-plot}
model <- run_model(specification = specification, 
                   dictionary = statcan_dict_ready, 
                   primary_source = "download",
                   quiet = TRUE, 
                   plot = FALSE)
```

```{r}
model
```

## Forecasting


```{r, forecast-plot-2}
forecast <- forecast_model(model = model, plot = FALSE)

plot(forecast)

```

