---
title: "Example Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
library(osem)
library(dplyr)
library(purrr)
```

# Setting up the Model

## Dictionary

In this illustration, we will rely on the default dictionary that is available
from `dict`.

```{r dictionary}
dict %>% 
  select(model_varname, database, dataset_id, variable_code, freq, geo) %>% 
  head()
dict %>% 
  select(model_varname, database, dataset_id, variable_code, freq, geo) %>% 
  tail()
```

## Specification

We use a specification for illustrative purposes only. Our specification
contains the following four modules/equations:

```{r specification}
specification <- dplyr::tibble(
    type = c(
      "d",
      "d",
      "n",
      "n"
    ),
    dependent = c(
      "StatDiscrep",
      "TOTS",
      "Import",
      "EmiCO2Combustion"
    ),
    independent = c(
      "TOTS - FinConsExpHH - FinConsExpGov - GCapitalForm - Export",
      "GValueAdd + Import",
      "FinConsExpHH + GCapitalForm",
      "HDD + HICP_Energy + GValueAdd"
    )
  )
print(specification)
```

The first two equations are simply accounting identities. The third equation
models imports as a function of final consumption expenditure of households and
gross capital formation. The fourth equation models carbon emissions from
combustion activities, which includes energy industries, manufacturing and 
construction, transport, and combustion activities in other sectors.The
regressors are the number of heating degree days, the harmonised
index of consumer prices for energy, and total gross value added.

## Data

We differentiate between where data can be obtained from *in principle* versus
where it should be obtained from *actually* in a specific model run. For 
example, a variable that is available on Eurostat can be downloaded from 
Eurostat but might have been saved locally from a previous model run. In order
to save time, the user might prefer that the local data is used rather than
re-downloading the data.

The dictionary specifies where the data for the different variables can be
obtained *in principle*. The column `dict$database` may take one of four
different values:

* `eurostat` if the variable is available from Eurostat using 
`eurostat::get_eurostat()`,
* `edgar` if the (emissions) variable is available EDGAR using a link,
* `local` if the variable is not available from the above two sources and is
therefore provided as a local file by the user in the directory 
`inputdata_directory`. This directory is searched for `.rds`, `.csv`,
and `.xlsx` files, opens them consecutively, and searches for the variable.
* `NA` if the variable is constructed as an identity/definition

The argument `primary_source` in the main function `run_model()` governs how the
data is *actually* obtained in this model run. Data that can in principle be
downloaded from `eurostat` or `edgar` can also be loaded locally if it has been
saved manually by the user or using the `save_to_disk` argument in `run_model()`
in a previous model run. The argument `primary_source` can take either the value
`"download"` or `"local"`, which governs whether download or local input takes
precedence for `eurostat` and `edgar` variables.

This gives rise to the following combinations of obtaining data:

* variables with `dictionary$database == "local"` are always searched for among
the local files of `inputdata_directory` and an error is raised if they cannot
be found there
* variables with `dictionary$database == "eurostat"` or 
`dictionary$database == "egdar"`
  * argument `primary_source == "download"` first downloads all the variables 
  (potentially updating the values) and only searches the local directory if 
  the variables cannot be obtained that way (e.g. if there were problems with 
  the download)
  * argument `primary_source == "local"` first searches the local directory and
  only downloads those variables that could not be found locally

Here, we use variables that can *in principle* all be obtained from either
Eurostat or EDGAR but we use the local file `example-workflow-data.rds` to save
time when compiling the vignette.

```{r dictionary$database}
vars <- c("StatDiscrep", "TOTS", "Import", "EmiCO2Combustion", "FinConsExpHH",
          "FinConsExpGov", "GCapitalForm", "Export", "GValueAdd", "HDD",
          "HICP_Energy")
dict %>% 
  filter(model_varname %in% vars) %>% 
  pull(database)
```
To avoid downloading all those variables again, we will specify 
`primary_source == "local"` and provide a `inputdata_directory` path to the
local directory when calling `run_model()`.

# Running the Model

We are now ready to run the model and obtain an `"osem"` object.


```{r, include=FALSE}
dat <- tibble::tribble(
         ~time,           ~na_item,     ~values,
  "1991-01-01",        "GValueAdd",    437661.5,
  "1991-04-01",        "GValueAdd",    433434.7,
  "1991-07-01",        "GValueAdd",    432813.1,
  "1991-10-01",        "GValueAdd",      439029,
  "1992-01-01",        "GValueAdd",    445851.8,
  "1992-04-01",        "GValueAdd",    442867.8,
  "1992-07-01",        "GValueAdd",    441935.4,
  "1992-10-01",        "GValueAdd",    439759.6,
  "1993-01-01",        "GValueAdd",    436900.1,
  "1993-04-01",        "GValueAdd",      436465,
  "1993-07-01",        "GValueAdd",    437894.8,
  "1993-10-01",        "GValueAdd",    437832.6,
  "1994-01-01",        "GValueAdd",    441345.1,
  "1994-04-01",        "GValueAdd",    445696.4,
  "1994-07-01",        "GValueAdd",    448369.3,
  "1994-10-01",        "GValueAdd",    454088.1,
  "1995-01-01",        "GValueAdd",    451819.2,
  "1995-04-01",        "GValueAdd",    456046.5,
  "1995-07-01",        "GValueAdd",    457165.5,
  "1995-10-01",        "GValueAdd",    458284.4,
  "1996-01-01",        "GValueAdd",      451493,
  "1996-04-01",        "GValueAdd",    460133.7,
  "1996-07-01",        "GValueAdd",    460382.4,
  "1996-10-01",        "GValueAdd",    466660.9,
  "1997-01-01",        "GValueAdd",      462714,
  "1997-04-01",        "GValueAdd",    468619.1,
  "1997-07-01",        "GValueAdd",    470608.2,
  "1997-10-01",        "GValueAdd",    476264.7,
  "1998-01-01",        "GValueAdd",    479186.8,
  "1998-04-01",        "GValueAdd",    476886.6,
  "1998-07-01",        "GValueAdd",    479373.3,
  "1998-10-01",        "GValueAdd",    480554.5,
  "1999-01-01",        "GValueAdd",      483989,
  "1999-04-01",        "GValueAdd",    483864.7,
  "1999-07-01",        "GValueAdd",    489956.6,
  "1999-10-01",        "GValueAdd",    492007.9,
  "2000-01-01",        "GValueAdd",    500306.7,
  "2000-04-01",        "GValueAdd",      504161,
  "2000-07-01",        "GValueAdd",    506274.6,
  "2000-10-01",        "GValueAdd",    504596.1,
  "2001-01-01",        "GValueAdd",    515583.5,
  "2001-04-01",        "GValueAdd",    513221.3,
  "2001-07-01",        "GValueAdd",    514588.9,
  "2001-10-01",        "GValueAdd",    514091.6,
  "2002-01-01",        "GValueAdd",    512040.2,
  "2002-04-01",        "GValueAdd",    514215.9,
  "2002-07-01",        "GValueAdd",    516080.8,
  "2002-10-01",        "GValueAdd",    517137.6,
  "2003-01-01",        "GValueAdd",      508932,
  "2003-04-01",        "GValueAdd",    508807.7,
  "2003-07-01",        "GValueAdd",    515024.1,
  "2003-10-01",        "GValueAdd",    515583.5,
  "2004-01-01",        "GValueAdd",    514604.3,
  "2004-04-01",        "GValueAdd",    520199.3,
  "2004-07-01",        "GValueAdd",    517526.1,
  "2004-10-01",        "GValueAdd",    517526.1,
  "2005-01-01",        "GValueAdd",    518691.7,
  "2005-04-01",        "GValueAdd",    520991.7,
  "2005-07-01",        "GValueAdd",    524472.9,
  "2005-10-01",        "GValueAdd",    527829.7,
  "2006-01-01",        "GValueAdd",    533315.3,
  "2006-04-01",        "GValueAdd",    542577.9,
  "2006-07-01",        "GValueAdd",    547737.7,
  "2006-10-01",        "GValueAdd",    555135.3,
  "2007-01-01",        "GValueAdd",    556751.1,
  "2007-04-01",        "GValueAdd",    562408.1,
  "2007-07-01",        "GValueAdd",    565081.2,
  "2007-10-01",        "GValueAdd",    569867.9,
  "2008-01-01",        "GValueAdd",    572898.2,
  "2008-04-01",        "GValueAdd",    571654.9,
  "2008-07-01",        "GValueAdd",    567614.3,
  "2008-10-01",        "GValueAdd",    557357.3,
  "2009-01-01",        "GValueAdd",    528948.7,
  "2009-04-01",        "GValueAdd",    530067.6,
  "2009-07-01",        "GValueAdd",    533362.2,
  "2009-10-01",        "GValueAdd",    537402.9,
  "2010-01-01",        "GValueAdd",      545904,
  "2010-04-01",        "GValueAdd",    554855.3,
  "2010-07-01",        "GValueAdd",      560139,
  "2010-10-01",        "GValueAdd",    563495.8,
  "2011-01-01",        "GValueAdd",      574701,
  "2011-04-01",        "GValueAdd",    575757.7,
  "2011-07-01",        "GValueAdd",    579611.9,
  "2011-10-01",        "GValueAdd",    579611.9,
  "2012-01-01",        "GValueAdd",    580761.8,
  "2012-04-01",        "GValueAdd",      581943,
  "2012-07-01",        "GValueAdd",    582937.7,
  "2012-10-01",        "GValueAdd",    580513.2,
  "2013-01-01",        "GValueAdd",    578430.8,
  "2013-04-01",        "GValueAdd",    584211.9,
  "2013-07-01",        "GValueAdd",    587257.9,
  "2013-10-01",        "GValueAdd",    589993.1,
  "2014-01-01",        "GValueAdd",    596644.6,
  "2014-04-01",        "GValueAdd",    594531.1,
  "2014-07-01",        "GValueAdd",    598136.5,
  "2014-10-01",        "GValueAdd",    602674.5,
  "2015-01-01",        "GValueAdd",    600374.5,
  "2015-04-01",        "GValueAdd",    604539.4,
  "2015-07-01",        "GValueAdd",    606590.8,
  "2015-10-01",        "GValueAdd",    608144.9,
  "2016-01-01",        "GValueAdd",    615790.9,
  "2016-04-01",        "GValueAdd",    618277.5,
  "2016-07-01",        "GValueAdd",    619209.9,
  "2016-10-01",        "GValueAdd",      621883,
  "2017-01-01",        "GValueAdd",    629218.3,
  "2017-04-01",        "GValueAdd",      635186,
  "2017-07-01",        "GValueAdd",    641464.5,
  "2017-10-01",        "GValueAdd",    646934.8,
  "2018-01-01",        "GValueAdd",    644494.9,
  "2018-04-01",        "GValueAdd",    647603.1,
  "2018-07-01",        "GValueAdd",    643624.7,
  "2018-10-01",        "GValueAdd",    648038.2,
  "2019-01-01",        "GValueAdd",    650540.3,
  "2019-04-01",        "GValueAdd",    649794.4,
  "2019-07-01",        "GValueAdd",    651534.9,
  "2019-10-01",        "GValueAdd",    651161.9,
  "2020-01-01",        "GValueAdd",    640221.2,
  "2020-04-01",        "GValueAdd",    578492.9,
  "2020-07-01",        "GValueAdd",      628348,
  "2020-10-01",        "GValueAdd",    633880.5,
  "2021-01-01",        "GValueAdd",    628922.6,
  "2021-04-01",        "GValueAdd",    642225.9,
  "2021-07-01",        "GValueAdd",    649810.1,
  "2021-10-01",        "GValueAdd",    652856.1,
  "2022-01-01",        "GValueAdd",    654223.5,
  "2022-04-01",        "GValueAdd",    651985.5,
  "2022-07-01",        "GValueAdd",    657518.2,
  "2022-10-01",        "GValueAdd",    657145.2,
  "2023-01-01",        "GValueAdd",      656850,
  "2023-04-01",        "GValueAdd",    655979.7,
  "2023-07-01",        "GValueAdd",      656477,
  "2023-10-01",        "GValueAdd",      663066,
  "2024-01-01",        "GValueAdd",    659756.1,
  "2024-04-01",        "GValueAdd",    657704.7,
  "2024-07-01",        "GValueAdd",    655218.1,
  "2024-10-01",        "GValueAdd",    653477.5,
  "2025-01-01",        "GValueAdd",    657207.3,
  "1991-01-01",           "Export",    101231.1,
  "1991-04-01",           "Export",     95359.5,
  "1991-07-01",           "Export",    100001.5,
  "1991-10-01",           "Export",    100155.2,
  "1992-01-01",           "Export",    101407.7,
  "1992-04-01",           "Export",     96489.5,
  "1992-07-01",           "Export",     99225.3,
  "1992-10-01",           "Export",     94614.4,
  "1993-01-01",           "Export",     91363.9,
  "1993-04-01",           "Export",     89334.9,
  "1993-07-01",           "Export",     89611.6,
  "1993-10-01",           "Export",     91240.9,
  "1994-01-01",           "Export",     94276.3,
  "1994-04-01",           "Export",     98610.5,
  "1994-07-01",           "Export",     98210.9,
  "1994-10-01",           "Export",     98764.2,
  "1995-01-01",           "Export",    102760.2,
  "1995-04-01",           "Export",    103528.7,
  "1995-07-01",           "Export",    104266.4,
  "1995-10-01",           "Export",    105895.6,
  "1996-01-01",           "Export",    107470.8,
  "1996-04-01",           "Export",    107778.2,
  "1996-07-01",           "Export",    110514.1,
  "1996-10-01",           "Export",      115402,
  "1997-01-01",           "Export",    117569.1,
  "1997-04-01",           "Export",    120980.9,
  "1997-07-01",           "Export",    127466.4,
  "1997-10-01",           "Export",      129157,
  "1998-01-01",           "Export",    132077.5,
  "1998-04-01",           "Export",    134136.9,
  "1998-07-01",           "Export",    132753.7,
  "1998-10-01",           "Export",    130479.2,
  "1999-01-01",           "Export",    131278.7,
  "1999-04-01",           "Export",    138071.6,
  "1999-07-01",           "Export",    141114.6,
  "1999-10-01",           "Export",    144003.9,
  "2000-01-01",           "Export",      150874,
  "2000-04-01",           "Export",      156315,
  "2000-07-01",           "Export",    158989.4,
  "2000-10-01",           "Export",    167289.4,
  "2001-01-01",           "Export",    166966.2,
  "2001-04-01",           "Export",      167458,
  "2001-07-01",           "Export",    167119.9,
  "2001-10-01",           "Export",    169179.3,
  "2002-01-01",           "Export",    168449.3,
  "2002-04-01",           "Export",    173521.2,
  "2002-07-01",           "Export",    176287.7,
  "2002-10-01",           "Export",    179453.8,
  "2003-01-01",           "Export",    174043.8,
  "2003-04-01",           "Export",    173306.1,
  "2003-07-01",           "Export",    178439.5,
  "2003-10-01",           "Export",    182742.9,
  "2004-01-01",           "Export",    190127.8,
  "2004-04-01",           "Export",    198427.6,
  "2004-07-01",           "Export",    194861.7,
  "2004-10-01",           "Export",    195876.2,
  "2005-01-01",           "Export",    200725.2,
  "2005-04-01",           "Export",    204260.2,
  "2005-07-01",           "Export",    212344.5,
  "2005-10-01",           "Export",    215572.1,
  "2006-01-01",           "Export",    222557.1,
  "2006-04-01",           "Export",    229412.1,
  "2006-07-01",           "Export",    235683.1,
  "2006-10-01",           "Export",    249208.7,
  "2007-01-01",           "Export",    247463.3,
  "2007-04-01",           "Export",    253672.9,
  "2007-07-01",           "Export",      258407,
  "2007-10-01",           "Export",    260743.3,
  "2008-01-01",           "Export",    263078.8,
  "2008-04-01",           "Export",    261972.2,
  "2008-07-01",           "Export",    259421.1,
  "2008-10-01",           "Export",    244820.9,
  "2009-01-01",           "Export",    216432.8,
  "2009-04-01",           "Export",    214649.9,
  "2009-07-01",           "Export",    221320.3,
  "2009-10-01",           "Export",    227683.2,
  "2010-01-01",           "Export",    234668.2,
  "2010-04-01",           "Export",    251267.7,
  "2010-07-01",           "Export",    255110.2,
  "2010-10-01",           "Export",    260059.3,
  "2011-01-01",           "Export",    266721.7,
  "2011-04-01",           "Export",    270348.8,
  "2011-07-01",           "Export",    273084.6,
  "2011-10-01",           "Export",    271639.9,
  "2012-01-01",           "Export",    277295.9,
  "2012-04-01",           "Export",    279416.8,
  "2012-07-01",           "Export",      282583,
  "2012-10-01",           "Export",    277726.2,
  "2013-01-01",           "Export",    276888.7,
  "2013-04-01",           "Export",    277780.1,
  "2013-07-01",           "Export",      282483,
  "2013-10-01",           "Export",    287124.5,
  "2014-01-01",           "Export",    287055.8,
  "2014-04-01",           "Export",    289668.5,
  "2014-07-01",           "Export",    294832.3,
  "2014-10-01",           "Export",    300303.6,
  "2015-01-01",           "Export",    302148.1,
  "2015-04-01",           "Export",    307343.3,
  "2015-07-01",           "Export",    307312.5,
  "2015-10-01",           "Export",    305560.3,
  "2016-01-01",           "Export",    308741.8,
  "2016-04-01",           "Export",    311969.4,
  "2016-07-01",           "Export",    311385.4,
  "2016-10-01",           "Export",    312399.7,
  "2017-01-01",           "Export",    319561.9,
  "2017-04-01",           "Export",    325002.7,
  "2017-07-01",           "Export",    328322.5,
  "2017-10-01",           "Export",    330812.3,
  "2018-01-01",           "Export",    335699.8,
  "2018-04-01",           "Export",    336222.4,
  "2018-07-01",           "Export",    333025.5,
  "2018-10-01",           "Export",    333486.6,
  "2019-01-01",           "Export",    343538.3,
  "2019-04-01",           "Export",    338281.9,
  "2019-07-01",           "Export",    342093.5,
  "2019-10-01",           "Export",      340157,
  "2020-01-01",           "Export",    331550.1,
  "2020-04-01",           "Export",    261895.7,
  "2020-07-01",           "Export",    308280.7,
  "2020-10-01",           "Export",    322451.4,
  "2021-01-01",           "Export",    332326.2,
  "2021-04-01",           "Export",    334570.1,
  "2021-07-01",           "Export",    331465.4,
  "2021-10-01",           "Export",    345790.1,
  "2022-01-01",           "Export",    343353.8,
  "2022-04-01",           "Export",    343999.3,
  "2022-07-01",           "Export",    349378.6,
  "2022-10-01",           "Export",    350454.5,
  "2023-01-01",           "Export",    350247.1,
  "2023-04-01",           "Export",    348986.8,
  "2023-07-01",           "Export",    346650.5,
  "2023-10-01",           "Export",    344037.7,
  "2024-01-01",           "Export",    344222.3,
  "2024-04-01",           "Export",    350523.9,
  "2024-07-01",           "Export",    341394.2,
  "2024-10-01",           "Export",    330727.6,
  "2025-01-01",           "Export",      341425,
  "1991-01-01",           "Import",     95272.2,
  "1991-04-01",           "Import",       95907,
  "1991-07-01",           "Import",       97149,
  "1991-10-01",           "Import",     96928.2,
  "1992-01-01",           "Import",    100295.4,
  "1992-04-01",           "Import",     97507.9,
  "1992-07-01",           "Import",     97038.7,
  "1992-10-01",           "Import",     98418.7,
  "1993-01-01",           "Import",     89013.6,
  "1993-04-01",           "Import",     89758.8,
  "1993-07-01",           "Import",     91028.5,
  "1993-10-01",           "Import",     91194.1,
  "1994-01-01",           "Import",     93077.6,
  "1994-04-01",           "Import",     97107.6,
  "1994-07-01",           "Import",     99039.8,
  "1994-10-01",           "Import",    100916.8,
  "1995-01-01",           "Import",      101358,
  "1995-04-01",           "Import",    104118.3,
  "1995-07-01",           "Import",    104891.2,
  "1995-10-01",           "Import",    106050.5,
  "1996-01-01",           "Import",    106402.3,
  "1996-04-01",           "Import",    107119.9,
  "1996-07-01",           "Import",    107865.2,
  "1996-10-01",           "Import",    112005.3,
  "1997-01-01",           "Import",    115283.2,
  "1997-04-01",           "Import",    116442.3,
  "1997-07-01",           "Import",    120278.7,
  "1997-10-01",           "Import",    121851.9,
  "1998-01-01",           "Import",    126461.6,
  "1998-04-01",           "Import",    129442.3,
  "1998-07-01",           "Import",    130215.1,
  "1998-10-01",           "Import",    129663.1,
  "1999-01-01",           "Import",    134941.9,
  "1999-04-01",           "Import",    139192.5,
  "1999-07-01",           "Import",      142615,
  "1999-10-01",           "Import",    142780.6,
  "2000-01-01",           "Import",    147638.4,
  "2000-04-01",           "Import",    151944.2,
  "2000-07-01",           "Import",    156884.8,
  "2000-10-01",           "Import",    165027.1,
  "2001-01-01",           "Import",    158727.1,
  "2001-04-01",           "Import",    159141.1,
  "2001-07-01",           "Import",    156022.3,
  "2001-10-01",           "Import",    154035.1,
  "2002-01-01",           "Import",    148687.2,
  "2002-04-01",           "Import",    151916.6,
  "2002-07-01",           "Import",      152165,
  "2002-10-01",           "Import",    155808.3,
  "2003-01-01",           "Import",    159072.2,
  "2003-04-01",           "Import",    157333.2,
  "2003-07-01",           "Import",    158575.3,
  "2003-10-01",           "Import",    163378.1,
  "2004-01-01",           "Import",    164806.3,
  "2004-04-01",           "Import",    168173.6,
  "2004-07-01",           "Import",    171458.2,
  "2004-10-01",           "Import",    172037.8,
  "2005-01-01",           "Import",    169271.2,
  "2005-04-01",           "Import",      177772,
  "2005-07-01",           "Import",    182436.4,
  "2005-10-01",           "Import",    189336.4,
  "2006-01-01",           "Import",    193891.2,
  "2006-04-01",           "Import",    196844.4,
  "2006-07-01",           "Import",      200460,
  "2006-10-01",           "Import",    206890.9,
  "2007-01-01",           "Import",    208857.7,
  "2007-04-01",           "Import",    209934.1,
  "2007-07-01",           "Import",    214543.5,
  "2007-10-01",           "Import",    214653.9,
  "2008-01-01",           "Import",    216068.5,
  "2008-04-01",           "Import",    213805.2,
  "2008-07-01",           "Import",    217779.9,
  "2008-10-01",           "Import",    210520.5,
  "2009-01-01",           "Import",    197548.3,
  "2009-04-01",           "Import",    187556.3,
  "2009-07-01",           "Import",    194015.2,
  "2009-10-01",           "Import",    192331.5,
  "2010-01-01",           "Import",    204959.4,
  "2010-04-01",           "Import",    219808.3,
  "2010-07-01",           "Import",    219201.1,
  "2010-10-01",           "Import",    221905.9,
  "2011-01-01",           "Import",    227550.4,
  "2011-04-01",           "Import",    233208.8,
  "2011-07-01",           "Import",    233181.2,
  "2011-10-01",           "Import",    230917.9,
  "2012-01-01",           "Import",    230835.1,
  "2012-04-01",           "Import",    231607.9,
  "2012-07-01",           "Import",      232298,
  "2012-10-01",           "Import",    230448.6,
  "2013-01-01",           "Import",    230979.7,
  "2013-04-01",           "Import",    234926.9,
  "2013-07-01",           "Import",      238460,
  "2013-10-01",           "Import",    238515.2,
  "2014-01-01",           "Import",    238936.2,
  "2014-04-01",           "Import",    242910.6,
  "2014-07-01",           "Import",    244345.8,
  "2014-10-01",           "Import",    248734.3,
  "2015-01-01",           "Import",    253178.2,
  "2015-04-01",           "Import",    253785.5,
  "2015-07-01",           "Import",    256269.5,
  "2015-10-01",           "Import",    259167.5,
  "2016-01-01",           "Import",    263783.9,
  "2016-04-01",           "Import",    262376.3,
  "2016-07-01",           "Import",    263866.7,
  "2016-10-01",           "Import",    269635.3,
  "2017-01-01",           "Import",    270518.6,
  "2017-04-01",           "Import",    277474.1,
  "2017-07-01",           "Import",    277722.5,
  "2017-10-01",           "Import",    281862.7,
  "2018-01-01",           "Import",    286306.4,
  "2018-04-01",           "Import",    287686.5,
  "2018-07-01",           "Import",    294310.8,
  "2018-10-01",           "Import",    296215.2,
  "2019-01-01",           "Import",    300838.4,
  "2019-04-01",           "Import",    297967.7,
  "2019-07-01",           "Import",    302356.5,
  "2019-10-01",           "Import",    304316.3,
  "2020-01-01",           "Import",    299085.7,
  "2020-04-01",           "Import",    246146.8,
  "2020-07-01",           "Import",    272450.7,
  "2020-10-01",           "Import",    282387.1,
  "2021-01-01",           "Import",    292185.5,
  "2021-04-01",           "Import",      294090,
  "2021-07-01",           "Import",    296242.8,
  "2021-10-01",           "Import",      314984,
  "2022-01-01",           "Import",    313024.3,
  "2022-04-01",           "Import",    319096.6,
  "2022-07-01",           "Import",    324920.4,
  "2022-10-01",           "Import",    325941.7,
  "2023-01-01",           "Import",    322629.5,
  "2023-04-01",           "Import",    324147.6,
  "2023-07-01",           "Import",    319731.4,
  "2023-10-01",           "Import",    313217.5,
  "2024-01-01",           "Import",    312279.1,
  "2024-04-01",           "Import",    320890.6,
  "2024-07-01",           "Import",    320614.6,
  "2024-10-01",           "Import",    318434.1,
  "2025-01-01",           "Import",    321856.7,
  "1991-01-01",     "GCapitalForm",    120898.5,
  "1991-04-01",     "GCapitalForm",    125156.5,
  "1991-07-01",     "GCapitalForm",    122388.8,
  "1991-10-01",     "GCapitalForm",      123652,
  "1992-01-01",     "GCapitalForm",    125621.2,
  "1992-04-01",     "GCapitalForm",    124826.4,
  "1992-07-01",     "GCapitalForm",    117375.1,
  "1992-10-01",     "GCapitalForm",    120696.3,
  "1993-01-01",     "GCapitalForm",    110708.5,
  "1993-04-01",     "GCapitalForm",    115972.9,
  "1993-07-01",     "GCapitalForm",    118158.1,
  "1993-10-01",     "GCapitalForm",    114312.7,
  "1994-01-01",     "GCapitalForm",    116530.3,
  "1994-04-01",     "GCapitalForm",    117410.3,
  "1994-07-01",     "GCapitalForm",    121597.5,
  "1994-10-01",     "GCapitalForm",    126139.5,
  "1995-01-01",     "GCapitalForm",    121835.2,
  "1995-04-01",     "GCapitalForm",    124007.3,
  "1995-07-01",     "GCapitalForm",    122388.9,
  "1995-10-01",     "GCapitalForm",    119705.7,
  "1996-01-01",     "GCapitalForm",    114699.7,
  "1996-04-01",     "GCapitalForm",    119638.6,
  "1996-07-01",     "GCapitalForm",    117396.2,
  "1996-10-01",     "GCapitalForm",      120334,
  "1997-01-01",     "GCapitalForm",      117744,
  "1997-04-01",     "GCapitalForm",    119787.8,
  "1997-07-01",     "GCapitalForm",    119518.1,
  "1997-10-01",     "GCapitalForm",    122910.2,
  "1998-01-01",     "GCapitalForm",    124684.6,
  "1998-04-01",     "GCapitalForm",    123577.6,
  "1998-07-01",     "GCapitalForm",    125947.8,
  "1998-10-01",     "GCapitalForm",    125252.3,
  "1999-01-01",     "GCapitalForm",    128485.2,
  "1999-04-01",     "GCapitalForm",    124395.5,
  "1999-07-01",     "GCapitalForm",    131197.4,
  "1999-10-01",     "GCapitalForm",    128215.4,
  "2000-01-01",     "GCapitalForm",    129723.1,
  "2000-04-01",     "GCapitalForm",    130432.9,
  "2000-07-01",     "GCapitalForm",    133300.8,
  "2000-10-01",     "GCapitalForm",    130063.8,
  "2001-01-01",     "GCapitalForm",    132225.3,
  "2001-04-01",     "GCapitalForm",    133176.3,
  "2001-07-01",     "GCapitalForm",    129343.7,
  "2001-10-01",     "GCapitalForm",    120826.8,
  "2002-01-01",     "GCapitalForm",    116115.1,
  "2002-04-01",     "GCapitalForm",    118158.7,
  "2002-07-01",     "GCapitalForm",    116682.8,
  "2002-10-01",     "GCapitalForm",    112893.7,
  "2003-01-01",     "GCapitalForm",    115941.5,
  "2003-04-01",     "GCapitalForm",    115359.5,
  "2003-07-01",     "GCapitalForm",      113230,
  "2003-10-01",     "GCapitalForm",    113641.7,
  "2004-01-01",     "GCapitalForm",    108195.5,
  "2004-04-01",     "GCapitalForm",    107003.6,
  "2004-07-01",     "GCapitalForm",    112324.7,
  "2004-10-01",     "GCapitalForm",    111161.1,
  "2005-01-01",     "GCapitalForm",    102336.6,
  "2005-04-01",     "GCapitalForm",    107744.4,
  "2005-07-01",     "GCapitalForm",    109334.1,
  "2005-10-01",     "GCapitalForm",    115323.9,
  "2006-01-01",     "GCapitalForm",    115870.5,
  "2006-04-01",     "GCapitalForm",    120511.6,
  "2006-07-01",     "GCapitalForm",    121760.6,
  "2006-10-01",     "GCapitalForm",      119731,
  "2007-01-01",     "GCapitalForm",    128307.5,
  "2007-04-01",     "GCapitalForm",    124461.1,
  "2007-07-01",     "GCapitalForm",    127881.7,
  "2007-10-01",     "GCapitalForm",    129726.9,
  "2008-01-01",     "GCapitalForm",    129859.2,
  "2008-04-01",     "GCapitalForm",    125598.7,
  "2008-07-01",     "GCapitalForm",    129092.3,
  "2008-10-01",     "GCapitalForm",    127601.2,
  "2009-01-01",     "GCapitalForm",      109547,
  "2009-04-01",     "GCapitalForm",    100803.7,
  "2009-07-01",     "GCapitalForm",    104494.1,
  "2009-10-01",     "GCapitalForm",    101002.4,
  "2010-01-01",     "GCapitalForm",    111240.9,
  "2010-04-01",     "GCapitalForm",    120152.7,
  "2010-07-01",     "GCapitalForm",    118889.7,
  "2010-10-01",     "GCapitalForm",    118832.9,
  "2011-01-01",     "GCapitalForm",    129812.1,
  "2011-04-01",     "GCapitalForm",    131543.7,
  "2011-07-01",     "GCapitalForm",    130919.2,
  "2011-10-01",     "GCapitalForm",    128463.7,
  "2012-01-01",     "GCapitalForm",    122562.7,
  "2012-04-01",     "GCapitalForm",    120859.4,
  "2012-07-01",     "GCapitalForm",    118389.7,
  "2012-10-01",     "GCapitalForm",    120334.2,
  "2013-01-01",     "GCapitalForm",    118181.7,
  "2013-04-01",     "GCapitalForm",    125991.4,
  "2013-07-01",     "GCapitalForm",      125892,
  "2013-10-01",     "GCapitalForm",    124486.2,
  "2014-01-01",     "GCapitalForm",      129833,
  "2014-04-01",     "GCapitalForm",      129606,
  "2014-07-01",     "GCapitalForm",    125859.6,
  "2014-10-01",     "GCapitalForm",    126895.5,
  "2015-01-01",     "GCapitalForm",    125830.7,
  "2015-04-01",     "GCapitalForm",    123318.9,
  "2015-07-01",     "GCapitalForm",    125362.4,
  "2015-10-01",     "GCapitalForm",    127349.1,
  "2016-01-01",     "GCapitalForm",      131203,
  "2016-04-01",     "GCapitalForm",    128804.6,
  "2016-07-01",     "GCapitalForm",    130677.9,
  "2016-10-01",     "GCapitalForm",    133289.2,
  "2017-01-01",     "GCapitalForm",    135204.9,
  "2017-04-01",     "GCapitalForm",    138782.4,
  "2017-07-01",     "GCapitalForm",    140769.8,
  "2017-10-01",     "GCapitalForm",    143467.1,
  "2018-01-01",     "GCapitalForm",    140407.1,
  "2018-04-01",     "GCapitalForm",    144282.4,
  "2018-07-01",     "GCapitalForm",    148470.1,
  "2018-10-01",     "GCapitalForm",    148711.4,
  "2019-01-01",     "GCapitalForm",      145088,
  "2019-04-01",     "GCapitalForm",    146266.2,
  "2019-07-01",     "GCapitalForm",    144662.2,
  "2019-10-01",     "GCapitalForm",    146379.8,
  "2020-01-01",     "GCapitalForm",    147804.5,
  "2020-04-01",     "GCapitalForm",    140156.1,
  "2020-07-01",     "GCapitalForm",    134054.3,
  "2020-10-01",     "GCapitalForm",    143575.9,
  "2021-01-01",     "GCapitalForm",    149605.3,
  "2021-04-01",     "GCapitalForm",    152117.6,
  "2021-07-01",     "GCapitalForm",    141074.6,
  "2021-10-01",     "GCapitalForm",    145829.7,
  "2022-01-01",     "GCapitalForm",    141927.2,
  "2022-04-01",     "GCapitalForm",    145361.5,
  "2022-07-01",     "GCapitalForm",    148526.1,
  "2022-10-01",     "GCapitalForm",    150583.9,
  "2023-01-01",     "GCapitalForm",    149214.5,
  "2023-04-01",     "GCapitalForm",    147468.8,
  "2023-07-01",     "GCapitalForm",      146078,
  "2023-10-01",     "GCapitalForm",      140160,
  "2024-01-01",     "GCapitalForm",    140500.4,
  "2024-04-01",     "GCapitalForm",    137875.1,
  "2024-07-01",     "GCapitalForm",    143310.1,
  "2024-10-01",     "GCapitalForm",    147595.6,
  "2025-01-01",     "GCapitalForm",    142884.4,
  "1991-01-01",    "FinConsExpGov",     81887.8,
  "1991-04-01",    "FinConsExpGov",     83172.2,
  "1991-07-01",    "FinConsExpGov",     85493.2,
  "1991-10-01",    "FinConsExpGov",     86313.4,
  "1992-01-01",    "FinConsExpGov",     87949.8,
  "1992-04-01",    "FinConsExpGov",     88847.2,
  "1992-07-01",    "FinConsExpGov",     90162.5,
  "1992-10-01",    "FinConsExpGov",     90348.1,
  "1993-01-01",    "FinConsExpGov",     90711.8,
  "1993-04-01",    "FinConsExpGov",     90309.5,
  "1993-07-01",    "FinConsExpGov",     90092.8,
  "1993-10-01",    "FinConsExpGov",     89953.6,
  "1994-01-01",    "FinConsExpGov",     92661.5,
  "1994-04-01",    "FinConsExpGov",     93326.9,
  "1994-07-01",    "FinConsExpGov",     93373.3,
  "1994-10-01",    "FinConsExpGov",     94549.4,
  "1995-01-01",    "FinConsExpGov",     93415.9,
  "1995-04-01",    "FinConsExpGov",     95087.1,
  "1995-07-01",    "FinConsExpGov",     96557.1,
  "1995-10-01",    "FinConsExpGov",     97980.7,
  "1996-01-01",    "FinConsExpGov",     96932.3,
  "1996-04-01",    "FinConsExpGov",     97984.5,
  "1996-07-01",    "FinConsExpGov",     99439.1,
  "1996-10-01",    "FinConsExpGov",     99377.2,
  "1997-01-01",    "FinConsExpGov",     99620.9,
  "1997-04-01",    "FinConsExpGov",    100255.3,
  "1997-07-01",    "FinConsExpGov",    100317.2,
  "1997-10-01",    "FinConsExpGov",     98537.7,
  "1998-01-01",    "FinConsExpGov",      102205,
  "1998-04-01",    "FinConsExpGov",    102700.2,
  "1998-07-01",    "FinConsExpGov",    102731.1,
  "1998-10-01",    "FinConsExpGov",    102390.7,
  "1999-01-01",    "FinConsExpGov",    105675.1,
  "1999-04-01",    "FinConsExpGov",    105009.7,
  "1999-07-01",    "FinConsExpGov",      105706,
  "1999-10-01",    "FinConsExpGov",    104963.3,
  "2000-01-01",    "FinConsExpGov",      107884,
  "2000-04-01",    "FinConsExpGov",    107342.4,
  "2000-07-01",    "FinConsExpGov",      106971,
  "2000-10-01",    "FinConsExpGov",    107791.1,
  "2001-01-01",    "FinConsExpGov",    107972.9,
  "2001-04-01",    "FinConsExpGov",    107586.1,
  "2001-07-01",    "FinConsExpGov",    107183.8,
  "2001-10-01",    "FinConsExpGov",    108777.5,
  "2002-01-01",    "FinConsExpGov",    108522.2,
  "2002-04-01",    "FinConsExpGov",    108909.1,
  "2002-07-01",    "FinConsExpGov",      109265,
  "2002-10-01",    "FinConsExpGov",      110766,
  "2003-01-01",    "FinConsExpGov",    109245.7,
  "2003-04-01",    "FinConsExpGov",    109400.4,
  "2003-07-01",    "FinConsExpGov",    110468.1,
  "2003-10-01",    "FinConsExpGov",    111179.9,
  "2004-01-01",    "FinConsExpGov",      109559,
  "2004-04-01",    "FinConsExpGov",    109357.8,
  "2004-07-01",    "FinConsExpGov",      110147,
  "2004-10-01",    "FinConsExpGov",    108769.8,
  "2005-01-01",    "FinConsExpGov",      109060,
  "2005-04-01",    "FinConsExpGov",    110622.8,
  "2005-07-01",    "FinConsExpGov",    110313.4,
  "2005-10-01",    "FinConsExpGov",    110328.8,
  "2006-01-01",    "FinConsExpGov",    111005.8,
  "2006-04-01",    "FinConsExpGov",    110959.4,
  "2006-07-01",    "FinConsExpGov",    111748.5,
  "2006-10-01",    "FinConsExpGov",      112058,
  "2007-01-01",    "FinConsExpGov",    112986.5,
  "2007-04-01",    "FinConsExpGov",    113450.7,
  "2007-07-01",    "FinConsExpGov",    113373.3,
  "2007-10-01",    "FinConsExpGov",    114286.2,
  "2008-01-01",    "FinConsExpGov",    116255.3,
  "2008-04-01",    "FinConsExpGov",      118530,
  "2008-07-01",    "FinConsExpGov",    117787.2,
  "2008-10-01",    "FinConsExpGov",    118762.1,
  "2009-01-01",    "FinConsExpGov",    120344.3,
  "2009-04-01",    "FinConsExpGov",    121210.8,
  "2009-07-01",    "FinConsExpGov",    122046.5,
  "2009-10-01",    "FinConsExpGov",    121891.7,
  "2010-01-01",    "FinConsExpGov",    123311.4,
  "2010-04-01",    "FinConsExpGov",    122321.1,
  "2010-07-01",    "FinConsExpGov",    123698.3,
  "2010-10-01",    "FinConsExpGov",    124007.7,
  "2011-01-01",    "FinConsExpGov",      123884,
  "2011-04-01",    "FinConsExpGov",      124472,
  "2011-07-01",    "FinConsExpGov",    124564.8,
  "2011-10-01",    "FinConsExpGov",    125292.1,
  "2012-01-01",    "FinConsExpGov",    125400.4,
  "2012-04-01",    "FinConsExpGov",      125942,
  "2012-07-01",    "FinConsExpGov",    126483.6,
  "2012-10-01",    "FinConsExpGov",    126762.1,
  "2013-01-01",    "FinConsExpGov",    127829.8,
  "2013-04-01",    "FinConsExpGov",    127613.2,
  "2013-07-01",    "FinConsExpGov",      128619,
  "2013-10-01",    "FinConsExpGov",    128665.4,
  "2014-01-01",    "FinConsExpGov",    129237.9,
  "2014-04-01",    "FinConsExpGov",    129934.2,
  "2014-07-01",    "FinConsExpGov",    130893.6,
  "2014-10-01",    "FinConsExpGov",    131822.1,
  "2015-01-01",    "FinConsExpGov",    132429.4,
  "2015-04-01",    "FinConsExpGov",    133203.1,
  "2015-07-01",    "FinConsExpGov",    134456.5,
  "2015-10-01",    "FinConsExpGov",    136777.7,
  "2016-01-01",    "FinConsExpGov",    138212.8,
  "2016-04-01",    "FinConsExpGov",    139404.3,
  "2016-07-01",    "FinConsExpGov",    139791.1,
  "2016-10-01",    "FinConsExpGov",    140982.6,
  "2017-01-01",    "FinConsExpGov",    140669.3,
  "2017-04-01",    "FinConsExpGov",    141396.5,
  "2017-07-01",    "FinConsExpGov",    141767.9,
  "2017-10-01",    "FinConsExpGov",    143423.6,
  "2018-01-01",    "FinConsExpGov",    142495.2,
  "2018-04-01",    "FinConsExpGov",    143377.2,
  "2018-07-01",    "FinConsExpGov",    143067.7,
  "2018-10-01",    "FinConsExpGov",    144181.8,
  "2019-01-01",    "FinConsExpGov",      146089,
  "2019-04-01",    "FinConsExpGov",    146460.4,
  "2019-07-01",    "FinConsExpGov",    148611.2,
  "2019-10-01",    "FinConsExpGov",    148719.6,
  "2020-01-01",    "FinConsExpGov",    151752.4,
  "2020-04-01",    "FinConsExpGov",    151566.8,
  "2020-07-01",    "FinConsExpGov",    158096.7,
  "2020-10-01",    "FinConsExpGov",    157539.7,
  "2021-01-01",    "FinConsExpGov",    157094.7,
  "2021-04-01",    "FinConsExpGov",    161551.3,
  "2021-07-01",    "FinConsExpGov",    160947.8,
  "2021-10-01",    "FinConsExpGov",    160468.1,
  "2022-01-01",    "FinConsExpGov",    162027.1,
  "2022-04-01",    "FinConsExpGov",    161980.7,
  "2022-07-01",    "FinConsExpGov",    158344.3,
  "2022-10-01",    "FinConsExpGov",    158545.5,
  "2023-01-01",    "FinConsExpGov",    159551.3,
  "2023-04-01",    "FinConsExpGov",    158870.4,
  "2023-07-01",    "FinConsExpGov",    160108.3,
  "2023-10-01",    "FinConsExpGov",    161470.1,
  "2024-01-01",    "FinConsExpGov",    162197.3,
  "2024-04-01",    "FinConsExpGov",    164595.8,
  "2024-07-01",    "FinConsExpGov",    166514.5,
  "2024-10-01",    "FinConsExpGov",    167241.8,
  "2025-01-01",    "FinConsExpGov",    166669.3,
  "1991-01-01",     "FinConsExpHH",      280780,
  "1991-04-01",     "FinConsExpHH",    280419.8,
  "1991-07-01",     "FinConsExpHH",    275881.2,
  "1991-10-01",     "FinConsExpHH",    280167.7,
  "1992-01-01",     "FinConsExpHH",    286102.1,
  "1992-04-01",     "FinConsExpHH",    285273.6,
  "1992-07-01",     "FinConsExpHH",    286570.3,
  "1992-10-01",     "FinConsExpHH",    288587.4,
  "1993-01-01",     "FinConsExpHH",    287434.8,
  "1993-04-01",     "FinConsExpHH",    285669.9,
  "1993-07-01",     "FinConsExpHH",    287578.9,
  "1993-10-01",     "FinConsExpHH",    289848.1,
  "1994-01-01",     "FinConsExpHH",    290289.5,
  "1994-04-01",     "FinConsExpHH",      291262,
  "1994-07-01",     "FinConsExpHH",    292378.7,
  "1994-10-01",     "FinConsExpHH",    293567.3,
  "1995-01-01",     "FinConsExpHH",    293324.1,
  "1995-04-01",     "FinConsExpHH",    295629.5,
  "1995-07-01",     "FinConsExpHH",    296710.2,
  "1995-10-01",     "FinConsExpHH",    297754.8,
  "1996-01-01",     "FinConsExpHH",    299105.5,
  "1996-04-01",     "FinConsExpHH",    300474.3,
  "1996-07-01",     "FinConsExpHH",    300942.5,
  "1996-10-01",     "FinConsExpHH",      301879,
  "1997-01-01",     "FinConsExpHH",    302968.7,
  "1997-04-01",     "FinConsExpHH",    303761.1,
  "1997-07-01",     "FinConsExpHH",    302968.7,
  "1997-10-01",     "FinConsExpHH",      305202,
  "1998-01-01",     "FinConsExpHH",    306687.8,
  "1998-04-01",     "FinConsExpHH",    305787.2,
  "1998-07-01",     "FinConsExpHH",    308092.6,
  "1998-10-01",     "FinConsExpHH",    310938.3,
  "1999-01-01",     "FinConsExpHH",    315359.8,
  "1999-04-01",     "FinConsExpHH",    316836.6,
  "1999-07-01",     "FinConsExpHH",    316728.5,
  "1999-10-01",     "FinConsExpHH",    320474.7,
  "2000-01-01",     "FinConsExpHH",    322554.9,
  "2000-04-01",     "FinConsExpHH",    325544.5,
  "2000-07-01",     "FinConsExpHH",    325544.5,
  "2000-10-01",     "FinConsExpHH",    325184.3,
  "2001-01-01",     "FinConsExpHH",    329020.6,
  "2001-04-01",     "FinConsExpHH",    326607.1,
  "2001-07-01",     "FinConsExpHH",    327975.9,
  "2001-10-01",     "FinConsExpHH",    329128.6,
  "2002-01-01",     "FinConsExpHH",    326679.2,
  "2002-04-01",     "FinConsExpHH",    324301.8,
  "2002-07-01",     "FinConsExpHH",    326715.2,
  "2002-10-01",     "FinConsExpHH",    328120.1,
  "2003-01-01",     "FinConsExpHH",    327705.8,
  "2003-04-01",     "FinConsExpHH",    327813.9,
  "2003-07-01",     "FinConsExpHH",    330047.1,
  "2003-10-01",     "FinConsExpHH",    330083.1,
  "2004-01-01",     "FinConsExpHH",    330263.2,
  "2004-04-01",     "FinConsExpHH",      329795,
  "2004-07-01",     "FinConsExpHH",    328822.5,
  "2004-10-01",     "FinConsExpHH",    330587.4,
  "2005-01-01",     "FinConsExpHH",    332550.5,
  "2005-04-01",     "FinConsExpHH",    333667.2,
  "2005-07-01",     "FinConsExpHH",    333631.2,
  "2005-10-01",     "FinConsExpHH",    333487.1,
  "2006-01-01",     "FinConsExpHH",    336422.8,
  "2006-04-01",     "FinConsExpHH",    338007.7,
  "2006-07-01",     "FinConsExpHH",    338007.7,
  "2006-10-01",     "FinConsExpHH",    341501.6,
  "2007-01-01",     "FinConsExpHH",    336602.9,
  "2007-04-01",     "FinConsExpHH",    338944.2,
  "2007-07-01",     "FinConsExpHH",      338620,
  "2007-10-01",     "FinConsExpHH",    338223.8,
  "2008-01-01",     "FinConsExpHH",    339124.3,
  "2008-04-01",     "FinConsExpHH",    337791.5,
  "2008-07-01",     "FinConsExpHH",    338007.6,
  "2008-10-01",     "FinConsExpHH",    336134.6,
  "2009-01-01",     "FinConsExpHH",    338881.2,
  "2009-04-01",     "FinConsExpHH",    340105.8,
  "2009-07-01",     "FinConsExpHH",    338989.2,
  "2009-10-01",     "FinConsExpHH",    339313.4,
  "2010-01-01",     "FinConsExpHH",    337287.3,
  "2010-04-01",     "FinConsExpHH",    340421.1,
  "2010-07-01",     "FinConsExpHH",    342077.9,
  "2010-10-01",     "FinConsExpHH",    343734.8,
  "2011-01-01",     "FinConsExpHH",    343023.5,
  "2011-04-01",     "FinConsExpHH",    344356.3,
  "2011-07-01",     "FinConsExpHH",      345689,
  "2011-10-01",     "FinConsExpHH",    346697.6,
  "2012-01-01",     "FinConsExpHH",    348426.6,
  "2012-04-01",     "FinConsExpHH",    349002.9,
  "2012-07-01",     "FinConsExpHH",    350047.5,
  "2012-10-01",     "FinConsExpHH",    348498.6,
  "2013-01-01",     "FinConsExpHH",    347490.1,
  "2013-04-01",     "FinConsExpHH",    350443.7,
  "2013-07-01",     "FinConsExpHH",    351740.5,
  "2013-10-01",     "FinConsExpHH",    349399.1,
  "2014-01-01",     "FinConsExpHH",    350596.8,
  "2014-04-01",     "FinConsExpHH",    351785.5,
  "2014-07-01",     "FinConsExpHH",    354487.1,
  "2014-10-01",     "FinConsExpHH",    356468.2,
  "2015-01-01",     "FinConsExpHH",      357981,
  "2015-04-01",     "FinConsExpHH",    359565.9,
  "2015-07-01",     "FinConsExpHH",    361691.2,
  "2015-10-01",     "FinConsExpHH",    364861.1,
  "2016-01-01",     "FinConsExpHH",    367229.3,
  "2016-04-01",     "FinConsExpHH",    366436.9,
  "2016-07-01",     "FinConsExpHH",    368129.8,
  "2016-10-01",     "FinConsExpHH",    371371.7,
  "2017-01-01",     "FinConsExpHH",      372101,
  "2017-04-01",     "FinConsExpHH",    374982.7,
  "2017-07-01",     "FinConsExpHH",    374658.5,
  "2017-10-01",     "FinConsExpHH",    378476.8,
  "2018-01-01",     "FinConsExpHH",    378611.8,
  "2018-04-01",     "FinConsExpHH",    379692.4,
  "2018-07-01",     "FinConsExpHH",    379332.2,
  "2018-10-01",     "FinConsExpHH",    383798.8,
  "2019-01-01",     "FinConsExpHH",    384663.3,
  "2019-04-01",     "FinConsExpHH",    385779.9,
  "2019-07-01",     "FinConsExpHH",      387797,
  "2019-10-01",     "FinConsExpHH",    389129.8,
  "2020-01-01",     "FinConsExpHH",      371453,
  "2020-04-01",     "FinConsExpHH",    332189.7,
  "2020-07-01",     "FinConsExpHH",    370336.4,
  "2020-10-01",     "FinConsExpHH",      364681,
  "2021-01-01",     "FinConsExpHH",      350219,
  "2021-04-01",     "FinConsExpHH",    360880.9,
  "2021-07-01",     "FinConsExpHH",    378458.5,
  "2021-10-01",     "FinConsExpHH",    381664.2,
  "2022-01-01",     "FinConsExpHH",    386797.4,
  "2022-04-01",     "FinConsExpHH",      387806,
  "2022-07-01",     "FinConsExpHH",    392740.9,
  "2022-10-01",     "FinConsExpHH",    386365.2,
  "2023-01-01",     "FinConsExpHH",    384915.4,
  "2023-04-01",     "FinConsExpHH",    389273.9,
  "2023-07-01",     "FinConsExpHH",    388949.7,
  "2023-10-01",     "FinConsExpHH",      387689,
  "2024-01-01",     "FinConsExpHH",    387400.8,
  "2024-04-01",     "FinConsExpHH",      387761,
  "2024-07-01",     "FinConsExpHH",    388805.6,
  "2024-10-01",     "FinConsExpHH",    389742.1,
  "2025-01-01",     "FinConsExpHH",    391651.2,
  "1991-01-01",      "StatDiscrep",           0,
  "1991-04-01",      "StatDiscrep",           0,
  "1991-07-01",      "StatDiscrep",           0,
  "1991-10-01",      "StatDiscrep",           0,
  "1992-01-01",      "StatDiscrep",           0,
  "1992-04-01",      "StatDiscrep",           0,
  "1992-07-01",      "StatDiscrep",           0,
  "1992-10-01",      "StatDiscrep",           0,
  "1993-01-01",      "StatDiscrep",           0,
  "1993-04-01",      "StatDiscrep",           0,
  "1993-07-01",      "StatDiscrep",           0,
  "1993-10-01",      "StatDiscrep",           0,
  "1994-01-01",      "StatDiscrep",           0,
  "1994-04-01",      "StatDiscrep",           0,
  "1994-07-01",      "StatDiscrep",           0,
  "1994-10-01",      "StatDiscrep",           0,
  "1995-01-01",      "StatDiscrep",           0,
  "1995-04-01",      "StatDiscrep",           0,
  "1995-07-01",      "StatDiscrep",           0,
  "1995-10-01",      "StatDiscrep",           0,
  "1996-01-01",      "StatDiscrep",           0,
  "1996-04-01",      "StatDiscrep",           0,
  "1996-07-01",      "StatDiscrep",           0,
  "1996-10-01",      "StatDiscrep",           0,
  "1997-01-01",      "StatDiscrep",           0,
  "1997-04-01",      "StatDiscrep",           0,
  "1997-07-01",      "StatDiscrep",           0,
  "1997-10-01",      "StatDiscrep",           0,
  "1998-01-01",      "StatDiscrep",           0,
  "1998-04-01",      "StatDiscrep",           0,
  "1998-07-01",      "StatDiscrep",           0,
  "1998-10-01",      "StatDiscrep",           0,
  "1999-01-01",      "StatDiscrep",           0,
  "1999-04-01",      "StatDiscrep",           0,
  "1999-07-01",      "StatDiscrep",           0,
  "1999-10-01",      "StatDiscrep",           0,
  "2000-01-01",      "StatDiscrep",           0,
  "2000-04-01",      "StatDiscrep",           0,
  "2000-07-01",      "StatDiscrep",           0,
  "2000-10-01",      "StatDiscrep",           0,
  "2001-01-01",      "StatDiscrep",           0,
  "2001-04-01",      "StatDiscrep",           0,
  "2001-07-01",      "StatDiscrep",           0,
  "2001-10-01",      "StatDiscrep",           0,
  "2002-01-01",      "StatDiscrep",           0,
  "2002-04-01",      "StatDiscrep",           0,
  "2002-07-01",      "StatDiscrep",           0,
  "2002-10-01",      "StatDiscrep",           0,
  "2003-01-01",      "StatDiscrep",           0,
  "2003-04-01",      "StatDiscrep",           0,
  "2003-07-01",      "StatDiscrep",           0,
  "2003-10-01",      "StatDiscrep",           0,
  "2004-01-01",      "StatDiscrep",           0,
  "2004-04-01",      "StatDiscrep",           0,
  "2004-07-01",      "StatDiscrep",           0,
  "2004-10-01",      "StatDiscrep",           0,
  "2005-01-01",      "StatDiscrep",           0,
  "2005-04-01",      "StatDiscrep",           0,
  "2005-07-01",      "StatDiscrep",           0,
  "2005-10-01",      "StatDiscrep",           0,
  "2006-01-01",      "StatDiscrep",           0,
  "2006-04-01",      "StatDiscrep",           0,
  "2006-07-01",      "StatDiscrep",           0,
  "2006-10-01",      "StatDiscrep",           0,
  "2007-01-01",      "StatDiscrep",           0,
  "2007-04-01",      "StatDiscrep",           0,
  "2007-07-01",      "StatDiscrep",           0,
  "2007-10-01",      "StatDiscrep",           0,
  "2008-01-01",      "StatDiscrep",           0,
  "2008-04-01",      "StatDiscrep",           0,
  "2008-07-01",      "StatDiscrep",           0,
  "2008-10-01",      "StatDiscrep",           0,
  "2009-01-01",      "StatDiscrep",           0,
  "2009-04-01",      "StatDiscrep",           0,
  "2009-07-01",      "StatDiscrep",           0,
  "2009-10-01",      "StatDiscrep",           0,
  "2010-01-01",      "StatDiscrep",           0,
  "2010-04-01",      "StatDiscrep",           0,
  "2010-07-01",      "StatDiscrep",           0,
  "2010-10-01",      "StatDiscrep",           0,
  "2011-01-01",      "StatDiscrep",           0,
  "2011-04-01",      "StatDiscrep",           0,
  "2011-07-01",      "StatDiscrep",           0,
  "2011-10-01",      "StatDiscrep",           0,
  "2012-01-01",      "StatDiscrep",           0,
  "2012-04-01",      "StatDiscrep",           0,
  "2012-07-01",      "StatDiscrep",           0,
  "2012-10-01",      "StatDiscrep",           0,
  "2013-01-01",      "StatDiscrep",           0,
  "2013-04-01",      "StatDiscrep",           0,
  "2013-07-01",      "StatDiscrep",           0,
  "2013-10-01",      "StatDiscrep",           0,
  "2014-01-01",      "StatDiscrep",           0,
  "2014-04-01",      "StatDiscrep",           0,
  "2014-07-01",      "StatDiscrep",           0,
  "2014-10-01",      "StatDiscrep",           0,
  "2015-01-01",      "StatDiscrep",           0,
  "2015-04-01",      "StatDiscrep",           0,
  "2015-07-01",      "StatDiscrep",           0,
  "2015-10-01",      "StatDiscrep",           0,
  "2016-01-01",      "StatDiscrep",           0,
  "2016-04-01",      "StatDiscrep",           0,
  "2016-07-01",      "StatDiscrep",           0,
  "2016-10-01",      "StatDiscrep",           0,
  "2017-01-01",      "StatDiscrep",           0,
  "2017-04-01",      "StatDiscrep",           0,
  "2017-07-01",      "StatDiscrep",           0,
  "2017-10-01",      "StatDiscrep",           0,
  "2018-01-01",      "StatDiscrep",           0,
  "2018-04-01",      "StatDiscrep",           0,
  "2018-07-01",      "StatDiscrep",           0,
  "2018-10-01",      "StatDiscrep",           0,
  "2019-01-01",      "StatDiscrep",           0,
  "2019-04-01",      "StatDiscrep",           0,
  "2019-07-01",      "StatDiscrep",           0,
  "2019-10-01",      "StatDiscrep",           0,
  "2020-01-01",      "StatDiscrep",           0,
  "2020-04-01",      "StatDiscrep",           0,
  "2020-07-01",      "StatDiscrep",           0,
  "2020-10-01",      "StatDiscrep",           0,
  "2021-01-01",      "StatDiscrep",           0,
  "2021-04-01",      "StatDiscrep",           0,
  "2021-07-01",      "StatDiscrep",           0,
  "2021-10-01",      "StatDiscrep",           0,
  "2022-01-01",      "StatDiscrep",           0,
  "1996-01-01",      "HICP_Energy",       151.9,
  "1996-04-01",      "HICP_Energy",       153.2,
  "1996-07-01",      "HICP_Energy",       153.7,
  "1996-10-01",      "HICP_Energy",       157.5,
  "1997-01-01",      "HICP_Energy",       158.6,
  "1997-04-01",      "HICP_Energy",         157,
  "1997-07-01",      "HICP_Energy",       158.7,
  "1997-10-01",      "HICP_Energy",         159,
  "1998-01-01",      "HICP_Energy",       154.7,
  "1998-04-01",      "HICP_Energy",       154.1,
  "1998-07-01",      "HICP_Energy",       153.1,
  "1998-10-01",      "HICP_Energy",         151,
  "1999-01-01",      "HICP_Energy",       149.4,
  "1999-04-01",      "HICP_Energy",         159,
  "1999-07-01",      "HICP_Energy",         164,
  "1999-10-01",      "HICP_Energy",         166,
  "2000-01-01",      "HICP_Energy",       173.5,
  "2000-04-01",      "HICP_Energy",       176.9,
  "2000-07-01",      "HICP_Energy",         186,
  "2000-10-01",      "HICP_Energy",       190.5,
  "2001-01-01",      "HICP_Energy",       190.9,
  "2001-04-01",      "HICP_Energy",       197.4,
  "2001-07-01",      "HICP_Energy",       193.8,
  "2001-10-01",      "HICP_Energy",       186.4,
  "2002-01-01",      "HICP_Energy",         190,
  "2002-04-01",      "HICP_Energy",       194.4,
  "2002-07-01",      "HICP_Energy",       193.5,
  "2002-10-01",      "HICP_Energy",       192.8,
  "2003-01-01",      "HICP_Energy",       204.3,
  "2003-04-01",      "HICP_Energy",       198.1,
  "2003-07-01",      "HICP_Energy",       199.4,
  "2003-10-01",      "HICP_Energy",       199.1,
  "2004-01-01",      "HICP_Energy",       201.1,
  "2004-04-01",      "HICP_Energy",         208,
  "2004-07-01",      "HICP_Energy",       211.7,
  "2004-10-01",      "HICP_Energy",       213.2,
  "2005-01-01",      "HICP_Energy",       214.7,
  "2005-04-01",      "HICP_Energy",       225.4,
  "2005-07-01",      "HICP_Energy",       239.1,
  "2005-10-01",      "HICP_Energy",       240.7,
  "2006-01-01",      "HICP_Energy",       244.6,
  "2006-04-01",      "HICP_Energy",         254,
  "2006-07-01",      "HICP_Energy",       253.9,
  "2006-10-01",      "HICP_Energy",         245,
  "2007-01-01",      "HICP_Energy",       250.5,
  "2007-04-01",      "HICP_Energy",       258.5,
  "2007-07-01",      "HICP_Energy",       260.8,
  "2007-10-01",      "HICP_Energy",       266.1,
  "2008-01-01",      "HICP_Energy",       274.1,
  "2008-04-01",      "HICP_Energy",       289.3,
  "2008-07-01",      "HICP_Energy",       294.9,
  "2008-10-01",      "HICP_Energy",       274.8,
  "2009-01-01",      "HICP_Energy",       268.1,
  "2009-04-01",      "HICP_Energy",       269.1,
  "2009-07-01",      "HICP_Energy",       268.1,
  "2009-10-01",      "HICP_Energy",       266.7,
  "2010-01-01",      "HICP_Energy",       272.6,
  "2010-04-01",      "HICP_Energy",       280.5,
  "2010-07-01",      "HICP_Energy",       278.4,
  "2010-10-01",      "HICP_Energy",       282.9,
  "2011-01-01",      "HICP_Energy",         299,
  "2011-04-01",      "HICP_Energy",       307.5,
  "2011-07-01",      "HICP_Energy",       307.8,
  "2011-10-01",      "HICP_Energy",       311.3,
  "2012-01-01",      "HICP_Energy",       320.3,
  "2012-04-01",      "HICP_Energy",       322.3,
  "2012-07-01",      "HICP_Energy",       326.7,
  "2012-10-01",      "HICP_Energy",       324.6,
  "2013-01-01",      "HICP_Energy",       330.4,
  "2013-04-01",      "HICP_Energy",       328.9,
  "2013-07-01",      "HICP_Energy",       331.8,
  "2013-10-01",      "HICP_Energy",       326.1,
  "2014-01-01",      "HICP_Energy",       323.9,
  "2014-04-01",      "HICP_Energy",       326.3,
  "2014-07-01",      "HICP_Energy",       325.6,
  "2014-10-01",      "HICP_Energy",       314.2,
  "2015-01-01",      "HICP_Energy",       300.5,
  "2015-04-01",      "HICP_Energy",       308.4,
  "2015-07-01",      "HICP_Energy",       300.9,
  "2015-10-01",      "HICP_Energy",       290.3,
  "2016-01-01",      "HICP_Energy",       277.2,
  "2016-04-01",      "HICP_Energy",       284.8,
  "2016-07-01",      "HICP_Energy",       284.3,
  "2016-10-01",      "HICP_Energy",       288.7,
  "2017-01-01",      "HICP_Energy",       294.1,
  "2017-04-01",      "HICP_Energy",       291.3,
  "2017-07-01",      "HICP_Energy",       289.7,
  "2017-10-01",      "HICP_Energy",       294.6,
  "2018-01-01",      "HICP_Energy",       295.3,
  "2018-04-01",      "HICP_Energy",       303.8,
  "2018-07-01",      "HICP_Energy",       310.5,
  "2018-10-01",      "HICP_Energy",       317.6,
  "2019-01-01",      "HICP_Energy",       305.6,
  "2019-04-01",      "HICP_Energy",       315.4,
  "2019-07-01",      "HICP_Energy",       312.3,
  "2019-10-01",      "HICP_Energy",       311.1,
  "2020-01-01",      "HICP_Energy",       310.4,
  "2020-04-01",      "HICP_Energy",       294.7,
  "2020-07-01",      "HICP_Energy",       292.5,
  "2020-10-01",      "HICP_Energy",       290.4,
  "2021-01-01",      "HICP_Energy",       312.9,
  "2021-04-01",      "HICP_Energy",       320.4,
  "2021-07-01",      "HICP_Energy",       328.5,
  "2021-10-01",      "HICP_Energy",       346.3,
  "2022-01-01",      "HICP_Energy",       397.2,
  "2022-04-01",      "HICP_Energy",       437.2,
  "2022-07-01",      "HICP_Energy",       455.2,
  "2022-10-01",      "HICP_Energy",       471.9,
  "2023-01-01",      "HICP_Energy",       464.7,
  "2023-04-01",      "HICP_Energy",       463.8,
  "2023-07-01",      "HICP_Energy",       467.7,
  "2023-10-01",      "HICP_Energy",       454.7,
  "2024-01-01",      "HICP_Energy",       451.6,
  "2024-04-01",      "HICP_Energy",       456.4,
  "2024-07-01",      "HICP_Energy",         445,
  "2024-10-01",      "HICP_Energy",       438.7,
  "2025-01-01",      "HICP_Energy",       443.7,
  "1979-01-01",              "HDD",     1680.89,
  "1979-04-01",              "HDD",      547.63,
  "1979-07-01",              "HDD",      230.25,
  "1979-10-01",              "HDD",        1120,
  "1980-01-01",              "HDD",     1526.24,
  "1980-04-01",              "HDD",      650.83,
  "1980-07-01",              "HDD",      194.07,
  "1980-10-01",              "HDD",     1272.41,
  "1981-01-01",              "HDD",     1443.18,
  "1981-04-01",              "HDD",      498.35,
  "1981-07-01",              "HDD",      171.77,
  "1981-10-01",              "HDD",     1313.31,
  "1982-01-01",              "HDD",     1529.73,
  "1982-04-01",              "HDD",      544.51,
  "1982-07-01",              "HDD",       68.44,
  "1982-10-01",              "HDD",     1072.23,
  "1983-01-01",              "HDD",      1375.8,
  "1983-04-01",              "HDD",      501.82,
  "1983-07-01",              "HDD",      120.24,
  "1983-10-01",              "HDD",     1217.61,
  "1984-01-01",              "HDD",     1515.18,
  "1984-04-01",              "HDD",      639.95,
  "1984-07-01",              "HDD",      231.48,
  "1984-10-01",              "HDD",     1118.72,
  "1985-01-01",              "HDD",     1766.87,
  "1985-04-01",              "HDD",      534.83,
  "1985-07-01",              "HDD",      154.75,
  "1985-10-01",              "HDD",     1208.77,
  "1986-01-01",              "HDD",     1682.82,
  "1986-04-01",              "HDD",      513.07,
  "1986-07-01",              "HDD",      279.58,
  "1986-10-01",              "HDD",     1081.53,
  "1987-01-01",              "HDD",      1805.8,
  "1987-04-01",              "HDD",      606.37,
  "1987-07-01",              "HDD",      168.64,
  "1987-10-01",              "HDD",     1121.85,
  "1988-01-01",              "HDD",     1348.45,
  "1988-04-01",              "HDD",      452.73,
  "1988-07-01",              "HDD",      153.44,
  "1988-10-01",              "HDD",     1134.73,
  "1989-01-01",              "HDD",     1197.54,
  "1989-04-01",              "HDD",      504.23,
  "1989-07-01",              "HDD",      147.42,
  "1989-10-01",              "HDD",     1135.85,
  "1990-01-01",              "HDD",     1127.19,
  "1990-04-01",              "HDD",      481.35,
  "1990-07-01",              "HDD",      210.54,
  "1990-10-01",              "HDD",      1138.5,
  "1991-01-01",              "HDD",     1409.78,
  "1991-04-01",              "HDD",      684.11,
  "1991-07-01",              "HDD",       79.72,
  "1991-10-01",              "HDD",     1229.47,
  "1992-01-01",              "HDD",     1345.05,
  "1992-04-01",              "HDD",      423.28,
  "1992-07-01",              "HDD",      113.61,
  "1992-10-01",              "HDD",     1224.49,
  "1993-01-01",              "HDD",     1423.18,
  "1993-04-01",              "HDD",      358.91,
  "1993-07-01",              "HDD",      244.86,
  "1993-10-01",              "HDD",     1270.96,
  "1994-01-01",              "HDD",     1308.78,
  "1994-04-01",              "HDD",      502.84,
  "1994-07-01",              "HDD",      135.55,
  "1994-10-01",              "HDD",     1057.29,
  "1995-01-01",              "HDD",     1351.34,
  "1995-04-01",              "HDD",      548.51,
  "1995-07-01",              "HDD",      152.69,
  "1995-10-01",              "HDD",     1211.96,
  "1996-01-01",              "HDD",     1729.44,
  "1996-04-01",              "HDD",      564.76,
  "1996-07-01",              "HDD",      260.03,
  "1996-10-01",              "HDD",     1268.06,
  "1997-01-01",              "HDD",     1375.15,
  "1997-04-01",              "HDD",         555,
  "1997-07-01",              "HDD",      112.22,
  "1997-10-01",              "HDD",     1186.04,
  "1998-01-01",              "HDD",     1239.37,
  "1998-04-01",              "HDD",      417.06,
  "1998-07-01",              "HDD",      190.87,
  "1998-10-01",              "HDD",     1287.88,
  "1999-01-01",              "HDD",     1336.13,
  "1999-04-01",              "HDD",       450.3,
  "1999-07-01",              "HDD",        43.1,
  "1999-10-01",              "HDD",      1174.1,
  "2000-01-01",              "HDD",     1306.52,
  "2000-04-01",              "HDD",      371.38,
  "2000-07-01",              "HDD",      151.82,
  "2000-10-01",              "HDD",     1012.55,
  "2001-01-01",              "HDD",     1376.65,
  "2001-04-01",              "HDD",      518.72,
  "2001-07-01",              "HDD",      187.96,
  "2001-10-01",              "HDD",     1133.41,
  "2002-01-01",              "HDD",     1259.94,
  "2002-04-01",              "HDD",      441.43,
  "2002-07-01",              "HDD",      141.08,
  "2002-10-01",              "HDD",     1210.53,
  "2003-01-01",              "HDD",     1495.64,
  "2003-04-01",              "HDD",      399.81,
  "2003-07-01",              "HDD",      113.27,
  "2003-10-01",              "HDD",     1213.12,
  "2004-01-01",              "HDD",     1409.86,
  "2004-04-01",              "HDD",      492.02,
  "2004-07-01",              "HDD",      134.15,
  "2004-10-01",              "HDD",      1138.1,
  "2005-01-01",              "HDD",     1435.61,
  "2005-04-01",              "HDD",      476.69,
  "2005-07-01",              "HDD",      124.67,
  "2005-10-01",              "HDD",     1112.09,
  "2006-01-01",              "HDD",     1628.71,
  "2006-04-01",              "HDD",      467.55,
  "2006-07-01",              "HDD",       49.51,
  "2006-10-01",              "HDD",      878.27,
  "2007-01-01",              "HDD",     1132.88,
  "2007-04-01",              "HDD",      311.62,
  "2007-07-01",              "HDD",      179.27,
  "2007-10-01",              "HDD",     1196.61,
  "2008-01-01",              "HDD",     1241.69,
  "2008-04-01",              "HDD",      431.69,
  "2008-07-01",              "HDD",      169.45,
  "2008-10-01",              "HDD",     1143.01,
  "2009-01-01",              "HDD",     1503.68,
  "2009-04-01",              "HDD",      360.51,
  "2009-07-01",              "HDD",       80.54,
  "2009-10-01",              "HDD",     1136.65,
  "2010-01-01",              "HDD",     1584.22,
  "2010-04-01",              "HDD",      535.98,
  "2010-07-01",              "HDD",      169.73,
  "2010-10-01",              "HDD",     1345.47,
  "2011-01-01",              "HDD",     1379.42,
  "2011-04-01",              "HDD",      319.26,
  "2011-07-01",              "HDD",      119.25,
  "2011-10-01",              "HDD",     1055.09,
  "2012-01-01",              "HDD",     1398.72,
  "2012-04-01",              "HDD",      456.36,
  "2012-07-01",              "HDD",      131.12,
  "2012-10-01",              "HDD",     1144.73,
  "2013-01-01",              "HDD",     1602.13,
  "2013-04-01",              "HDD",      519.26,
  "2013-07-01",              "HDD",      134.47,
  "2013-10-01",              "HDD",      1033.2,
  "2014-01-01",              "HDD",     1177.58,
  "2014-04-01",              "HDD",      404.89,
  "2014-07-01",              "HDD",      116.04,
  "2014-10-01",              "HDD",      960.49,
  "2015-01-01",              "HDD",     1337.65,
  "2015-04-01",              "HDD",      494.33,
  "2015-07-01",              "HDD",      144.73,
  "2015-10-01",              "HDD",      931.71,
  "2016-01-01",              "HDD",     1352.24,
  "2016-04-01",              "HDD",      421.56,
  "2016-07-01",              "HDD",       61.32,
  "2016-10-01",              "HDD",      1173.9,
  "2017-01-01",              "HDD",     1348.93,
  "2017-04-01",              "HDD",      435.13,
  "2017-07-01",              "HDD",      148.65,
  "2017-10-01",              "HDD",     1033.12,
  "2018-01-01",              "HDD",     1448.44,
  "2018-04-01",              "HDD",      235.06,
  "2018-07-01",              "HDD",       87.83,
  "2018-10-01",              "HDD",     1003.62,
  "2019-01-01",              "HDD",     1242.92,
  "2019-04-01",              "HDD",      444.15,
  "2019-07-01",              "HDD",      106.72,
  "2019-10-01",              "HDD",     1007.02,
  "2020-01-01",              "HDD",     1184.19,
  "2020-04-01",              "HDD",      435.96,
  "2020-07-01",              "HDD",       100.6,
  "2020-10-01",              "HDD",     1020.28,
  "2021-01-01",              "HDD",     1368.49,
  "2021-04-01",              "HDD",      565.71,
  "2021-07-01",              "HDD",       83.38,
  "2021-10-01",              "HDD",     1096.61,
  "2022-01-01",              "HDD",     1218.79,
  "2022-04-01",              "HDD",       418.1,
  "2022-07-01",              "HDD",      122.68,
  "2022-10-01",              "HDD",      977.14,
  "2023-01-01",              "HDD",      1202.4,
  "2023-04-01",              "HDD",      452.49,
  "2023-07-01",              "HDD",        45.8,
  "2023-10-01",              "HDD",      961.19,
  "2024-01-01",              "HDD",     1133.76,
  "2024-04-01",              "HDD",      322.59,
  "2024-07-01",              "HDD",       83.66,
  "2024-10-01",              "HDD",     1028.74,
  "1970-01-01", "EmiCO2Combustion", 315959.2508,
  "1970-04-01", "EmiCO2Combustion", 217938.6763,
  "1970-07-01", "EmiCO2Combustion", 182441.9371,
  "1970-10-01", "EmiCO2Combustion",  270439.704,
  "1971-01-01", "EmiCO2Combustion", 311759.4265,
  "1971-04-01", "EmiCO2Combustion", 214597.1071,
  "1971-07-01", "EmiCO2Combustion", 184555.2462,
  "1971-10-01", "EmiCO2Combustion", 271927.9195,
  "1972-01-01", "EmiCO2Combustion", 306081.8865,
  "1972-04-01", "EmiCO2Combustion",  223257.973,
  "1972-07-01", "EmiCO2Combustion", 193654.1412,
  "1972-10-01", "EmiCO2Combustion", 283424.4236,
  "1973-01-01", "EmiCO2Combustion",  323183.368,
  "1973-04-01", "EmiCO2Combustion", 235987.2834,
  "1973-07-01", "EmiCO2Combustion", 195154.2959,
  "1973-10-01", "EmiCO2Combustion", 303009.4951,
  "1974-01-01", "EmiCO2Combustion", 306492.2935,
  "1974-04-01", "EmiCO2Combustion", 234539.8137,
  "1974-07-01", "EmiCO2Combustion", 198693.9638,
  "1974-10-01", "EmiCO2Combustion", 291409.3072,
  "1975-01-01", "EmiCO2Combustion", 294323.2906,
  "1975-04-01", "EmiCO2Combustion", 222231.9152,
  "1975-07-01", "EmiCO2Combustion", 178630.9187,
  "1975-10-01", "EmiCO2Combustion", 283529.9879,
  "1976-01-01", "EmiCO2Combustion", 322394.7015,
  "1976-04-01", "EmiCO2Combustion", 226876.1586,
  "1976-07-01", "EmiCO2Combustion", 194527.6614,
  "1976-10-01", "EmiCO2Combustion", 291155.4936,
  "1977-01-01", "EmiCO2Combustion", 307274.0779,
  "1977-04-01", "EmiCO2Combustion",  231835.317,
  "1977-07-01", "EmiCO2Combustion", 197407.8412,
  "1977-10-01", "EmiCO2Combustion", 282462.9079,
  "1978-01-01", "EmiCO2Combustion", 318807.5533,
  "1978-04-01", "EmiCO2Combustion", 234927.2836,
  "1978-07-01", "EmiCO2Combustion", 205374.0388,
  "1978-10-01", "EmiCO2Combustion", 292597.7072,
  "1979-01-01", "EmiCO2Combustion", 348353.3223,
  "1979-04-01", "EmiCO2Combustion", 240950.3723,
  "1979-07-01", "EmiCO2Combustion",  210818.626,
  "1979-10-01", "EmiCO2Combustion", 298926.8432,
  "1980-01-01", "EmiCO2Combustion", 319043.1442,
  "1980-04-01", "EmiCO2Combustion", 236024.4551,
  "1980-07-01", "EmiCO2Combustion",  200796.662,
  "1980-10-01", "EmiCO2Combustion", 292286.4314,
  "1981-01-01", "EmiCO2Combustion", 307203.8184,
  "1981-04-01", "EmiCO2Combustion", 223172.4507,
  "1981-07-01", "EmiCO2Combustion", 195139.6548,
  "1981-10-01", "EmiCO2Combustion", 290351.0165,
  "1982-01-01", "EmiCO2Combustion", 305063.7118,
  "1982-04-01", "EmiCO2Combustion", 218884.1473,
  "1982-07-01", "EmiCO2Combustion", 183004.5915,
  "1982-10-01", "EmiCO2Combustion", 267574.6962,
  "1983-01-01", "EmiCO2Combustion", 294605.8292,
  "1983-04-01", "EmiCO2Combustion", 217781.1306,
  "1983-07-01", "EmiCO2Combustion", 186714.8774,
  "1983-10-01", "EmiCO2Combustion", 276978.0405,
  "1984-01-01", "EmiCO2Combustion", 303492.6226,
  "1984-04-01", "EmiCO2Combustion",  225741.947,
  "1984-07-01", "EmiCO2Combustion", 195175.6009,
  "1984-10-01", "EmiCO2Combustion", 271269.7972,
  "1985-01-01", "EmiCO2Combustion", 318690.7306,
  "1985-04-01", "EmiCO2Combustion", 219555.0137,
  "1985-07-01", "EmiCO2Combustion", 190127.4258,
  "1985-10-01", "EmiCO2Combustion", 275882.9277,
  "1986-01-01", "EmiCO2Combustion", 319436.1183,
  "1986-04-01", "EmiCO2Combustion", 219503.4338,
  "1986-07-01", "EmiCO2Combustion", 196293.3967,
  "1986-10-01", "EmiCO2Combustion", 271726.3952,
  "1987-01-01", "EmiCO2Combustion",  319204.411,
  "1987-04-01", "EmiCO2Combustion", 220795.7212,
  "1987-07-01", "EmiCO2Combustion", 188895.5353,
  "1987-10-01", "EmiCO2Combustion",  268237.778,
  "1988-01-01", "EmiCO2Combustion",  300700.395,
  "1988-04-01", "EmiCO2Combustion", 218401.7577,
  "1988-07-01", "EmiCO2Combustion", 192479.0497,
  "1988-10-01", "EmiCO2Combustion", 278039.2445,
  "1989-01-01", "EmiCO2Combustion", 283562.6126,
  "1989-04-01", "EmiCO2Combustion", 219310.5227,
  "1989-07-01", "EmiCO2Combustion", 190556.6878,
  "1989-10-01", "EmiCO2Combustion", 272367.9501,
  "1990-01-01", "EmiCO2Combustion", 271850.7956,
  "1990-04-01", "EmiCO2Combustion", 211509.4419,
  "1990-07-01", "EmiCO2Combustion",   189257.06,
  "1990-10-01", "EmiCO2Combustion", 267390.3866,
  "1991-01-01", "EmiCO2Combustion", 273551.8172,
  "1991-04-01", "EmiCO2Combustion", 211930.7975,
  "1991-07-01", "EmiCO2Combustion", 175103.9506,
  "1991-10-01", "EmiCO2Combustion", 257057.5971,
  "1992-01-01", "EmiCO2Combustion", 262365.0602,
  "1992-04-01", "EmiCO2Combustion", 193306.9517,
  "1992-07-01", "EmiCO2Combustion", 171402.0331,
  "1992-10-01", "EmiCO2Combustion", 250527.4965,
  "1993-01-01", "EmiCO2Combustion", 260796.1747,
  "1993-04-01", "EmiCO2Combustion", 187206.6246,
  "1993-07-01", "EmiCO2Combustion", 176142.4951,
  "1993-10-01", "EmiCO2Combustion", 247676.6093,
  "1994-01-01", "EmiCO2Combustion", 257625.5944,
  "1994-04-01", "EmiCO2Combustion", 194652.4497,
  "1994-07-01", "EmiCO2Combustion", 168689.1085,
  "1994-10-01", "EmiCO2Combustion", 238139.2397,
  "1995-01-01", "EmiCO2Combustion", 253492.2694,
  "1995-04-01", "EmiCO2Combustion", 192997.0441,
  "1995-07-01", "EmiCO2Combustion", 168015.9787,
  "1995-10-01", "EmiCO2Combustion", 242091.6229,
  "1996-01-01", "EmiCO2Combustion", 273396.4302,
  "1996-04-01", "EmiCO2Combustion", 194104.9563,
  "1996-07-01", "EmiCO2Combustion", 175446.5356,
  "1996-10-01", "EmiCO2Combustion", 244114.1796,
  "1997-01-01", "EmiCO2Combustion", 255746.1296,
  "1997-04-01", "EmiCO2Combustion", 192750.4797,
  "1997-07-01", "EmiCO2Combustion",  164933.444,
  "1997-10-01", "EmiCO2Combustion", 241489.6615,
  "1998-01-01", "EmiCO2Combustion", 246496.2198,
  "1998-04-01", "EmiCO2Combustion", 185508.2922,
  "1998-07-01", "EmiCO2Combustion", 169959.6438,
  "1998-10-01", "EmiCO2Combustion", 244979.6987,
  "1999-01-01", "EmiCO2Combustion", 243344.2561,
  "1999-04-01", "EmiCO2Combustion", 182050.6226,
  "1999-07-01", "EmiCO2Combustion",  158533.349,
  "1999-10-01", "EmiCO2Combustion", 231031.1456,
  "2000-01-01", "EmiCO2Combustion", 243785.3149,
  "2000-04-01", "EmiCO2Combustion", 179303.5753,
  "2000-07-01", "EmiCO2Combustion", 165110.2274,
  "2000-10-01", "EmiCO2Combustion", 224112.4915,
  "2001-01-01", "EmiCO2Combustion", 247401.3228,
  "2001-04-01", "EmiCO2Combustion", 188362.7824,
  "2001-07-01", "EmiCO2Combustion",  160292.351,
  "2001-10-01", "EmiCO2Combustion", 235422.7621,
  "2002-01-01", "EmiCO2Combustion", 237357.0563,
  "2002-04-01", "EmiCO2Combustion", 183934.9094,
  "2002-07-01", "EmiCO2Combustion", 161796.7479,
  "2002-10-01", "EmiCO2Combustion", 234813.1866,
  "2003-01-01", "EmiCO2Combustion", 246652.0347,
  "2003-04-01", "EmiCO2Combustion", 179337.4731,
  "2003-07-01", "EmiCO2Combustion", 164150.0575,
  "2003-10-01", "EmiCO2Combustion", 230548.8317,
  "2004-01-01", "EmiCO2Combustion", 238813.7467,
  "2004-04-01", "EmiCO2Combustion", 180122.9598,
  "2004-07-01", "EmiCO2Combustion", 162121.4667,
  "2004-10-01", "EmiCO2Combustion", 223566.7427,
  "2005-01-01", "EmiCO2Combustion", 231799.6998,
  "2005-04-01", "EmiCO2Combustion", 179357.7425,
  "2005-07-01", "EmiCO2Combustion", 155448.6487,
  "2005-10-01", "EmiCO2Combustion", 220325.4836,
  "2006-01-01", "EmiCO2Combustion", 258774.4482,
  "2006-04-01", "EmiCO2Combustion", 176522.7093,
  "2006-07-01", "EmiCO2Combustion", 152560.4805,
  "2006-10-01", "EmiCO2Combustion", 210824.2183,
  "2007-01-01", "EmiCO2Combustion", 211077.7689,
  "2007-04-01", "EmiCO2Combustion", 170206.7548,
  "2007-07-01", "EmiCO2Combustion",  162134.306,
  "2007-10-01", "EmiCO2Combustion", 223600.6134,
  "2008-01-01", "EmiCO2Combustion", 222646.1092,
  "2008-04-01", "EmiCO2Combustion", 177770.6169,
  "2008-07-01", "EmiCO2Combustion", 156822.3736,
  "2008-10-01", "EmiCO2Combustion", 216654.0862,
  "2009-01-01", "EmiCO2Combustion", 218341.5393,
  "2009-04-01", "EmiCO2Combustion", 152801.6933,
  "2009-07-01", "EmiCO2Combustion",  145587.059,
  "2009-10-01", "EmiCO2Combustion", 203451.8674,
  "2010-01-01", "EmiCO2Combustion", 225069.9528,
  "2010-04-01", "EmiCO2Combustion", 170428.4186,
  "2010-07-01", "EmiCO2Combustion", 147378.0532,
  "2010-10-01", "EmiCO2Combustion", 215971.9513,
  "2011-01-01", "EmiCO2Combustion", 215632.7025,
  "2011-04-01", "EmiCO2Combustion", 162571.0888,
  "2011-07-01", "EmiCO2Combustion", 148629.7802,
  "2011-10-01", "EmiCO2Combustion", 204408.0237,
  "2012-01-01", "EmiCO2Combustion", 220430.2187,
  "2012-04-01", "EmiCO2Combustion", 167934.4471,
  "2012-07-01", "EmiCO2Combustion", 149894.7885,
  "2012-10-01", "EmiCO2Combustion", 206882.1391,
  "2013-01-01", "EmiCO2Combustion", 236369.8544,
  "2013-04-01", "EmiCO2Combustion", 170694.6265,
  "2013-07-01", "EmiCO2Combustion", 153672.1944,
  "2013-10-01", "EmiCO2Combustion",  202915.136,
  "2014-01-01", "EmiCO2Combustion", 210385.3333,
  "2014-04-01", "EmiCO2Combustion", 162823.9862,
  "2014-07-01", "EmiCO2Combustion", 148055.6526,
  "2014-10-01", "EmiCO2Combustion", 201846.7588,
  "2015-01-01", "EmiCO2Combustion", 217726.7331,
  "2015-04-01", "EmiCO2Combustion", 161357.7723,
  "2015-07-01", "EmiCO2Combustion", 151347.5264,
  "2015-10-01", "EmiCO2Combustion", 199252.3698,
  "2016-01-01", "EmiCO2Combustion", 213279.9471,
  "2016-04-01", "EmiCO2Combustion", 161908.3333,
  "2016-07-01", "EmiCO2Combustion", 147096.4864,
  "2016-10-01", "EmiCO2Combustion", 212202.3868,
  "2017-01-01", "EmiCO2Combustion", 214263.5152,
  "2017-04-01", "EmiCO2Combustion", 163534.2815,
  "2017-07-01", "EmiCO2Combustion", 149488.2187,
  "2017-10-01", "EmiCO2Combustion", 191508.1581,
  "2018-01-01", "EmiCO2Combustion", 214806.0654,
  "2018-04-01", "EmiCO2Combustion", 151468.6977,
  "2018-07-01", "EmiCO2Combustion", 141726.7265,
  "2018-10-01", "EmiCO2Combustion", 186538.6611,
  "2019-01-01", "EmiCO2Combustion",  192040.381,
  "2019-04-01", "EmiCO2Combustion", 147227.9541,
  "2019-07-01", "EmiCO2Combustion", 131162.9058,
  "2019-10-01", "EmiCO2Combustion", 174972.2707,
  "2020-01-01", "EmiCO2Combustion", 176183.1695,
  "2020-04-01", "EmiCO2Combustion", 134711.7834,
  "2020-07-01", "EmiCO2Combustion", 118426.7956,
  "2020-10-01", "EmiCO2Combustion", 163774.9534,
  "2021-01-01", "EmiCO2Combustion",   186227.25,
  "2021-04-01", "EmiCO2Combustion", 144225.2657,
  "2021-07-01", "EmiCO2Combustion", 124876.3903,
  "2021-10-01", "EmiCO2Combustion", 168760.4006,
  "2022-01-01", "EmiCO2Combustion", 182956.5457,
  "2022-04-01", "EmiCO2Combustion", 139386.7467,
  "2022-07-01", "EmiCO2Combustion",  124839.515,
  "2022-10-01", "EmiCO2Combustion", 166549.9458,
  "2023-01-01", "EmiCO2Combustion", 161156.3995,
  "2023-04-01", "EmiCO2Combustion", 121920.9554,
  "2023-07-01", "EmiCO2Combustion", 108013.8317,
  "2023-10-01", "EmiCO2Combustion", 147474.1009
  )

```



```{r run-model, eval = FALSE}
model <- run_model(specification = specification,
                   dictionary = dict,
                   inputdata_directory = NULL,
                   primary_source = "local",
                   save_to_disk = "./Downloaded_Input.xlsx",
                   present = FALSE,
                   quiet = FALSE, 
                   plot = FALSE)
class(model)
```


```{r run-model-true, include = FALSE}
model <- run_model(specification = specification,
                   dictionary = dict,
                   inputdata_directory = dat,
                   primary_source = "local",
                   present = FALSE,
                   quiet = FALSE, 
                   plot = FALSE)
class(model)
```

```{r, fig.width=7, fig.height=5}
plot(model)
```


We did not `quiet` the output, so we get some information about the estimation.

We are told that local files are used, namely the file 
`"example-workflow-data.rds"`, which can be found in our working directory 
`"."` from where the vignette is created. Next, we obtain a warning that the 
panel is unbalanced, which means that we have "ragged edges" that cause more
than 20\% of the data to be discarded when limiting the sample to the time
periods that are available for **all** variables.

Finally, the estimation begins. The order of the modules is determined by how
they are related to each other, starting with the modules that only depend on
exogenous (unmodelled) variables and then gradually estimating the other modules
in order to avoid any reverse dependencies.

# Evaluating the Model

Now, we can have a look at the model results.

## Individual Module Results

The different modules are stored in `model$module_collection`, which is a tibble
that stores the datasets, independent and dependent variables, model arguments,
and the model itself as an `"isat"` object.

For example, taking a closer look at the estimated module for carbon emissions
from combustion activities:

```{r module emissions}
# extract the isat model object
co2module <- model$module_collection %>% 
  filter(dependent == "EmiCO2Combustion") %>% 
  pull(model) %>% 
  pluck(1)
class(co2module)
# inspect the estimated equation
print(co2module)
```
We find that the number of heating degree days (`HDD`) and gross value added
(`GValueAdd`) are significant, while gets model selection dropped the harmonised
consumer price index for energy. Both gross value added and heating degree days
have a positive coefficient meaning that they increase emissions, as we would
expect.

Both diagnostic tests of no autocorrelation and no autoregressive conditional
heteroskedasticity pass.

## Module Network

We can show the relationship between the different modules using the `network()`
function.

```{r network, fig.width=7, fig.height=5}
network(model)
```
Each node represents a module and the different colours represent whether the
variable is given by a definition/identity, whether it has been modelled as an
endogenous variable depending on other models, and whether it is an exogenous
variable input to the models.

An solid line arrow means that the variable has been retained during model
selection, while a dashed arrow means that the variable has been dropped during
model selection. Note again that `HICP_Energy` was in the original specification
but has been found to be insignificant.

## Forecasts

We can use our model to forecast the variables of our modules. This works for
both the definition/identity modules and the endogenous modules. The user can
either provide future values for the exogenous variables (e.g. corresponding to
certain scenario assumptions) or use automatic AR models to forecast future
values of the exogenous variables.

```{r, forecast}
forecast <- forecast_model(model = model,
                           exog_predictions = NULL,
                           plot = FALSE)
class(forecast)
```
We did not specify paths for the exogenous regressors, so the output informs us
that AR(4) processes were used to project their paths. The function returns an
object of class `"osem.forecast"`, which can also be plotted.

```{r, forecast-plot, fig.width=7, fig.height=5}
plot(forecast)
```

## Diagnostics

To obtain an overview of the diagnostic results for each endogenous module, we
can use the command `diagnostics_model()`. This avoids having to look at all
`"isat"` model objects manually.

```{r, diagnostics}
diagnostics_model(model)
```

The diagnostics pass for both modules: we neither have evidence for 
autocorrelated errors nor for autoregressive conditional heteroskedasticity.

The output also shows how many impulse indicators (representing outliers) and
step indicators (representing structural breaks of the mean) have been retained
in each module, both in absolute and as a share of the observations.

## Shiny App

Last but not least, we can get an overview and summary of the whole OSEM
model results in a Shiny app, which can be opened using the `present_model()`
command. The following code snippet is not executed:

```{r, shiny, eval=FALSE}
present_model(model)
```


