---
title: "Example Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
library(osem)
library(dplyr)
library(purrr)
```

# Setting up the Model

## Dictionary

In this illustration, we will rely on the default dictionary that is available
from `dict`.

```{r dictionary}
dict %>% 
  select(model_varname, database, dataset_id, variable_code, freq, geo) %>% 
  head()
dict %>% 
  select(model_varname, database, dataset_id, variable_code, freq, geo) %>% 
  tail()
```

## Specification

We use a specification for illustrative purposes only. Our specification
contains the following four modules/equations:

```{r specification}
specification <- dplyr::tibble(
    type = c(
      "d",
      "d",
      "n",
      "n"
    ),
    dependent = c(
      "StatDiscrep",
      "TOTS",
      "Import",
      "EmiCO2Combustion"
    ),
    independent = c(
      "TOTS - FinConsExpHH - FinConsExpGov - GCapitalForm - Export",
      "GValueAdd + Import",
      "FinConsExpHH + GCapitalForm",
      "HDD + HICP_Energy + GValueAdd"
    ),
    lag = "",
    cvar = ""
  )
print(specification)
```

The first two equations are simply accounting identities. The third equation
models imports as a function of final consumption expenditure of households and
gross capital formation. The fourth equation models carbon emissions from
combustion activities, which includes energy industries, manufacturing and 
construction, transport, and combustion activities in other sectors.The
regressors are the number of heating degree days, the harmonised
index of consumer prices for energy, and total gross value added.

## Data

We differentiate between where data can be obtained from *in principle* versus
where it should be obtained from *actually* in a specific model run. For 
example, a variable that is available on Eurostat can be downloaded from 
Eurostat but might have been saved locally from a previous model run. In order
to save time, the user might prefer that the local data is used rather than
re-downloading the data.

The dictionary specifies where the data for the different variables can be
obtained *in principle*. The column `dict$database` may take one of four
different values:

* `eurostat` if the variable is available from Eurostat using 
`eurostat::get_eurostat()`,
* `edgar` if the (emissions) variable is available EDGAR using a link,
* `local` if the variable is not available from the above two sources and is
therefore provided as a local file by the user in the directory 
`inputdata_directory`. This directory is searched for `.rds`, `.csv`,
and `.xlsx` files, opens them consecutively, and searches for the variable.
* `NA` if the variable is constructed as an identity/definition

The argument `primary_source` in the main function `run_model()` governs how the
data is *actually* obtained in this model run. Data that can in principle be
downloaded from `eurostat` or `edgar` can also be loaded locally if it has been
saved manually by the user or using the `save_to_disk` argument in `run_model()`
in a previous model run. The argument `primary_source` can take either the value
`"download"` or `"local"`, which governs whether download or local input takes
precedence for `eurostat` and `edgar` variables.

This gives rise to the following combinations of obtaining data:

* variables with `dictionary$database == "local"` are always searched for among
the local files of `inputdata_directory` and an error is raised if they cannot
be found there
* variables with `dictionary$database == "eurostat"` or 
`dictionary$database == "egdar"`
  * argument `primary_source == "download"` first downloads all the variables 
  (potentially updating the values) and only searches the local directory if 
  the variables cannot be obtained that way (e.g. if there were problems with 
  the download)
  * argument `primary_source == "local"` first searches the local directory and
  only downloads those variables that could not be found locally

Here, we use variables that can *in principle* all be obtained from either
Eurostat or EDGAR but we use the local file `example-workflow-data.rds` to save
time when compiling the vignette.

```{r dictionary$database}
vars <- c("StatDiscrep", "TOTS", "Import", "EmiCO2Combustion", "FinConsExpHH",
          "FinConsExpGov", "GCapitalForm", "Export", "GValueAdd", "HDD",
          "HICP_Energy")
dict %>% 
  filter(model_varname %in% vars) %>% 
  pull(database)
```
To avoid downloading all those variables again, we will specify 
`primary_source == "local"` and provide a `inputdata_directory` path to the
local directory when calling `run_model()`.

# Running the Model

We are now ready to run the model and obtain an `"osem"` object.


```{r, include=FALSE}
dat <- structure(list(time = c("1991-01-01", "1991-04-01", "1991-07-01", 
"1991-10-01", "1992-01-01", "1992-04-01", "1992-07-01", "1992-10-01", 
"1993-01-01", "1993-04-01", "1993-07-01", "1993-10-01", "1994-01-01", 
"1994-04-01", "1994-07-01", "1994-10-01", "1995-01-01", "1995-04-01", 
"1995-07-01", "1995-10-01", "1996-01-01", "1996-04-01", "1996-07-01", 
"1996-10-01", "1997-01-01", "1997-04-01", "1997-07-01", "1997-10-01", 
"1998-01-01", "1998-04-01", "1998-07-01", "1998-10-01", "1999-01-01", 
"1999-04-01", "1999-07-01", "1999-10-01", "2000-01-01", "2000-04-01", 
"2000-07-01", "2000-10-01", "2001-01-01", "2001-04-01", "2001-07-01", 
"2001-10-01", "2002-01-01", "2002-04-01", "2002-07-01", "2002-10-01", 
"2003-01-01", "2003-04-01", "2003-07-01", "2003-10-01", "2004-01-01", 
"2004-04-01", "2004-07-01", "2004-10-01", "2005-01-01", "2005-04-01", 
"2005-07-01", "2005-10-01", "2006-01-01", "2006-04-01", "2006-07-01", 
"2006-10-01", "2007-01-01", "2007-04-01", "2007-07-01", "2007-10-01", 
"2008-01-01", "2008-04-01", "2008-07-01", "2008-10-01", "2009-01-01", 
"2009-04-01", "2009-07-01", "2009-10-01", "2010-01-01", "2010-04-01", 
"2010-07-01", "2010-10-01", "2011-01-01", "2011-04-01", "2011-07-01", 
"2011-10-01", "2012-01-01", "2012-04-01", "2012-07-01", "2012-10-01", 
"2013-01-01", "2013-04-01", "2013-07-01", "2013-10-01", "2014-01-01", 
"2014-04-01", "2014-07-01", "2014-10-01", "2015-01-01", "2015-04-01", 
"2015-07-01", "2015-10-01", "2016-01-01", "2016-04-01", "2016-07-01", 
"2016-10-01", "2017-01-01", "2017-04-01", "2017-07-01", "2017-10-01", 
"2018-01-01", "2018-04-01", "2018-07-01", "2018-10-01", "2019-01-01", 
"2019-04-01", "2019-07-01", "2019-10-01", "2020-01-01", "2020-04-01", 
"2020-07-01", "2020-10-01", "2021-01-01", "2021-04-01", "2021-07-01", 
"2021-10-01", "2022-01-01", "2022-04-01", "2022-07-01", "2022-10-01", 
"2023-01-01", "2023-04-01", "2023-07-01", "2023-10-01", "2024-01-01", 
"2024-04-01", "2024-07-01", "2024-10-01", "2025-01-01", "1991-01-01", 
"1991-04-01", "1991-07-01", "1991-10-01", "1992-01-01", "1992-04-01", 
"1992-07-01", "1992-10-01", "1993-01-01", "1993-04-01", "1993-07-01", 
"1993-10-01", "1994-01-01", "1994-04-01", "1994-07-01", "1994-10-01", 
"1995-01-01", "1995-04-01", "1995-07-01", "1995-10-01", "1996-01-01", 
"1996-04-01", "1996-07-01", "1996-10-01", "1997-01-01", "1997-04-01", 
"1997-07-01", "1997-10-01", "1998-01-01", "1998-04-01", "1998-07-01", 
"1998-10-01", "1999-01-01", "1999-04-01", "1999-07-01", "1999-10-01", 
"2000-01-01", "2000-04-01", "2000-07-01", "2000-10-01", "2001-01-01", 
"2001-04-01", "2001-07-01", "2001-10-01", "2002-01-01", "2002-04-01", 
"2002-07-01", "2002-10-01", "2003-01-01", "2003-04-01", "2003-07-01", 
"2003-10-01", "2004-01-01", "2004-04-01", "2004-07-01", "2004-10-01", 
"2005-01-01", "2005-04-01", "2005-07-01", "2005-10-01", "2006-01-01", 
"2006-04-01", "2006-07-01", "2006-10-01", "2007-01-01", "2007-04-01", 
"2007-07-01", "2007-10-01", "2008-01-01", "2008-04-01", "2008-07-01", 
"2008-10-01", "2009-01-01", "2009-04-01", "2009-07-01", "2009-10-01", 
"2010-01-01", "2010-04-01", "2010-07-01", "2010-10-01", "2011-01-01", 
"2011-04-01", "2011-07-01", "2011-10-01", "2012-01-01", "2012-04-01", 
"2012-07-01", "2012-10-01", "2013-01-01", "2013-04-01", "2013-07-01", 
"2013-10-01", "2014-01-01", "2014-04-01", "2014-07-01", "2014-10-01", 
"2015-01-01", "2015-04-01", "2015-07-01", "2015-10-01", "2016-01-01", 
"2016-04-01", "2016-07-01", "2016-10-01", "2017-01-01", "2017-04-01", 
"2017-07-01", "2017-10-01", "2018-01-01", "2018-04-01", "2018-07-01", 
"2018-10-01", "2019-01-01", "2019-04-01", "2019-07-01", "2019-10-01", 
"2020-01-01", "2020-04-01", "2020-07-01", "2020-10-01", "2021-01-01", 
"2021-04-01", "2021-07-01", "2021-10-01", "2022-01-01", "2022-04-01", 
"2022-07-01", "2022-10-01", "2023-01-01", "2023-04-01", "2023-07-01", 
"2023-10-01", "2024-01-01", "2024-04-01", "2024-07-01", "2024-10-01", 
"2025-01-01", "1991-01-01", "1991-04-01", "1991-07-01", "1991-10-01", 
"1992-01-01", "1992-04-01", "1992-07-01", "1992-10-01", "1993-01-01", 
"1993-04-01", "1993-07-01", "1993-10-01", "1994-01-01", "1994-04-01", 
"1994-07-01", "1994-10-01", "1995-01-01", "1995-04-01", "1995-07-01", 
"1995-10-01", "1996-01-01", "1996-04-01", "1996-07-01", "1996-10-01", 
"1997-01-01", "1997-04-01", "1997-07-01", "1997-10-01", "1998-01-01", 
"1998-04-01", "1998-07-01", "1998-10-01", "1999-01-01", "1999-04-01", 
"1999-07-01", "1999-10-01", "2000-01-01", "2000-04-01", "2000-07-01", 
"2000-10-01", "2001-01-01", "2001-04-01", "2001-07-01", "2001-10-01", 
"2002-01-01", "2002-04-01", "2002-07-01", "2002-10-01", "2003-01-01", 
"2003-04-01", "2003-07-01", "2003-10-01", "2004-01-01", "2004-04-01", 
"2004-07-01", "2004-10-01", "2005-01-01", "2005-04-01", "2005-07-01", 
"2005-10-01", "2006-01-01", "2006-04-01", "2006-07-01", "2006-10-01", 
"2007-01-01", "2007-04-01", "2007-07-01", "2007-10-01", "2008-01-01", 
"2008-04-01", "2008-07-01", "2008-10-01", "2009-01-01", "2009-04-01", 
"2009-07-01", "2009-10-01", "2010-01-01", "2010-04-01", "2010-07-01", 
"2010-10-01", "2011-01-01", "2011-04-01", "2011-07-01", "2011-10-01", 
"2012-01-01", "2012-04-01", "2012-07-01", "2012-10-01", "2013-01-01", 
"2013-04-01", "2013-07-01", "2013-10-01", "2014-01-01", "2014-04-01", 
"2014-07-01", "2014-10-01", "2015-01-01", "2015-04-01", "2015-07-01", 
"2015-10-01", "2016-01-01", "2016-04-01", "2016-07-01", "2016-10-01", 
"2017-01-01", "2017-04-01", "2017-07-01", "2017-10-01", "2018-01-01", 
"2018-04-01", "2018-07-01", "2018-10-01", "2019-01-01", "2019-04-01", 
"2019-07-01", "2019-10-01", "2020-01-01", "2020-04-01", "2020-07-01", 
"2020-10-01", "2021-01-01", "2021-04-01", "2021-07-01", "2021-10-01", 
"2022-01-01", "2022-04-01", "2022-07-01", "2022-10-01", "2023-01-01", 
"2023-04-01", "2023-07-01", "2023-10-01", "2024-01-01", "2024-04-01", 
"2024-07-01", "2024-10-01", "2025-01-01", "1991-01-01", "1991-04-01", 
"1991-07-01", "1991-10-01", "1992-01-01", "1992-04-01", "1992-07-01", 
"1992-10-01", "1993-01-01", "1993-04-01", "1993-07-01", "1993-10-01", 
"1994-01-01", "1994-04-01", "1994-07-01", "1994-10-01", "1995-01-01", 
"1995-04-01", "1995-07-01", "1995-10-01", "1996-01-01", "1996-04-01", 
"1996-07-01", "1996-10-01", "1997-01-01", "1997-04-01", "1997-07-01", 
"1997-10-01", "1998-01-01", "1998-04-01", "1998-07-01", "1998-10-01", 
"1999-01-01", "1999-04-01", "1999-07-01", "1999-10-01", "2000-01-01", 
"2000-04-01", "2000-07-01", "2000-10-01", "2001-01-01", "2001-04-01", 
"2001-07-01", "2001-10-01", "2002-01-01", "2002-04-01", "2002-07-01", 
"2002-10-01", "2003-01-01", "2003-04-01", "2003-07-01", "2003-10-01", 
"2004-01-01", "2004-04-01", "2004-07-01", "2004-10-01", "2005-01-01", 
"2005-04-01", "2005-07-01", "2005-10-01", "2006-01-01", "2006-04-01", 
"2006-07-01", "2006-10-01", "2007-01-01", "2007-04-01", "2007-07-01", 
"2007-10-01", "2008-01-01", "2008-04-01", "2008-07-01", "2008-10-01", 
"2009-01-01", "2009-04-01", "2009-07-01", "2009-10-01", "2010-01-01", 
"2010-04-01", "2010-07-01", "2010-10-01", "2011-01-01", "2011-04-01", 
"2011-07-01", "2011-10-01", "2012-01-01", "2012-04-01", "2012-07-01", 
"2012-10-01", "2013-01-01", "2013-04-01", "2013-07-01", "2013-10-01", 
"2014-01-01", "2014-04-01", "2014-07-01", "2014-10-01", "2015-01-01", 
"2015-04-01", "2015-07-01", "2015-10-01", "2016-01-01", "2016-04-01", 
"2016-07-01", "2016-10-01", "2017-01-01", "2017-04-01", "2017-07-01", 
"2017-10-01", "2018-01-01", "2018-04-01", "2018-07-01", "2018-10-01", 
"2019-01-01", "2019-04-01", "2019-07-01", "2019-10-01", "2020-01-01", 
"2020-04-01", "2020-07-01", "2020-10-01", "2021-01-01", "2021-04-01", 
"2021-07-01", "2021-10-01", "2022-01-01", "2022-04-01", "2022-07-01", 
"2022-10-01", "2023-01-01", "2023-04-01", "2023-07-01", "2023-10-01", 
"2024-01-01", "2024-04-01", "2024-07-01", "2024-10-01", "2025-01-01", 
"1991-01-01", "1991-04-01", "1991-07-01", "1991-10-01", "1992-01-01", 
"1992-04-01", "1992-07-01", "1992-10-01", "1993-01-01", "1993-04-01", 
"1993-07-01", "1993-10-01", "1994-01-01", "1994-04-01", "1994-07-01", 
"1994-10-01", "1995-01-01", "1995-04-01", "1995-07-01", "1995-10-01", 
"1996-01-01", "1996-04-01", "1996-07-01", "1996-10-01", "1997-01-01", 
"1997-04-01", "1997-07-01", "1997-10-01", "1998-01-01", "1998-04-01", 
"1998-07-01", "1998-10-01", "1999-01-01", "1999-04-01", "1999-07-01", 
"1999-10-01", "2000-01-01", "2000-04-01", "2000-07-01", "2000-10-01", 
"2001-01-01", "2001-04-01", "2001-07-01", "2001-10-01", "2002-01-01", 
"2002-04-01", "2002-07-01", "2002-10-01", "2003-01-01", "2003-04-01", 
"2003-07-01", "2003-10-01", "2004-01-01", "2004-04-01", "2004-07-01", 
"2004-10-01", "2005-01-01", "2005-04-01", "2005-07-01", "2005-10-01", 
"2006-01-01", "2006-04-01", "2006-07-01", "2006-10-01", "2007-01-01", 
"2007-04-01", "2007-07-01", "2007-10-01", "2008-01-01", "2008-04-01", 
"2008-07-01", "2008-10-01", "2009-01-01", "2009-04-01", "2009-07-01", 
"2009-10-01", "2010-01-01", "2010-04-01", "2010-07-01", "2010-10-01", 
"2011-01-01", "2011-04-01", "2011-07-01", "2011-10-01", "2012-01-01", 
"2012-04-01", "2012-07-01", "2012-10-01", "2013-01-01", "2013-04-01", 
"2013-07-01", "2013-10-01", "2014-01-01", "2014-04-01", "2014-07-01", 
"2014-10-01", "2015-01-01", "2015-04-01", "2015-07-01", "2015-10-01", 
"2016-01-01", "2016-04-01", "2016-07-01", "2016-10-01", "2017-01-01", 
"2017-04-01", "2017-07-01", "2017-10-01", "2018-01-01", "2018-04-01", 
"2018-07-01", "2018-10-01", "2019-01-01", "2019-04-01", "2019-07-01", 
"2019-10-01", "2020-01-01", "2020-04-01", "2020-07-01", "2020-10-01", 
"2021-01-01", "2021-04-01", "2021-07-01", "2021-10-01", "2022-01-01", 
"2022-04-01", "2022-07-01", "2022-10-01", "2023-01-01", "2023-04-01", 
"2023-07-01", "2023-10-01", "2024-01-01", "2024-04-01", "2024-07-01", 
"2024-10-01", "2025-01-01", "1991-01-01", "1991-04-01", "1991-07-01", 
"1991-10-01", "1992-01-01", "1992-04-01", "1992-07-01", "1992-10-01", 
"1993-01-01", "1993-04-01", "1993-07-01", "1993-10-01", "1994-01-01", 
"1994-04-01", "1994-07-01", "1994-10-01", "1995-01-01", "1995-04-01", 
"1995-07-01", "1995-10-01", "1996-01-01", "1996-04-01", "1996-07-01", 
"1996-10-01", "1997-01-01", "1997-04-01", "1997-07-01", "1997-10-01", 
"1998-01-01", "1998-04-01", "1998-07-01", "1998-10-01", "1999-01-01", 
"1999-04-01", "1999-07-01", "1999-10-01", "2000-01-01", "2000-04-01", 
"2000-07-01", "2000-10-01", "2001-01-01", "2001-04-01", "2001-07-01", 
"2001-10-01", "2002-01-01", "2002-04-01", "2002-07-01", "2002-10-01", 
"2003-01-01", "2003-04-01", "2003-07-01", "2003-10-01", "2004-01-01", 
"2004-04-01", "2004-07-01", "2004-10-01", "2005-01-01", "2005-04-01", 
"2005-07-01", "2005-10-01", "2006-01-01", "2006-04-01", "2006-07-01", 
"2006-10-01", "2007-01-01", "2007-04-01", "2007-07-01", "2007-10-01", 
"2008-01-01", "2008-04-01", "2008-07-01", "2008-10-01", "2009-01-01", 
"2009-04-01", "2009-07-01", "2009-10-01", "2010-01-01", "2010-04-01", 
"2010-07-01", "2010-10-01", "2011-01-01", "2011-04-01", "2011-07-01", 
"2011-10-01", "2012-01-01", "2012-04-01", "2012-07-01", "2012-10-01", 
"2013-01-01", "2013-04-01", "2013-07-01", "2013-10-01", "2014-01-01", 
"2014-04-01", "2014-07-01", "2014-10-01", "2015-01-01", "2015-04-01", 
"2015-07-01", "2015-10-01", "2016-01-01", "2016-04-01", "2016-07-01", 
"2016-10-01", "2017-01-01", "2017-04-01", "2017-07-01", "2017-10-01", 
"2018-01-01", "2018-04-01", "2018-07-01", "2018-10-01", "2019-01-01", 
"2019-04-01", "2019-07-01", "2019-10-01", "2020-01-01", "2020-04-01", 
"2020-07-01", "2020-10-01", "2021-01-01", "2021-04-01", "2021-07-01", 
"2021-10-01", "2022-01-01", "2022-04-01", "2022-07-01", "2022-10-01", 
"2023-01-01", "2023-04-01", "2023-07-01", "2023-10-01", "2024-01-01", 
"2024-04-01", "2024-07-01", "2024-10-01", "2025-01-01", "1991-01-01", 
"1991-04-01", "1991-07-01", "1991-10-01", "1992-01-01", "1992-04-01", 
"1992-07-01", "1992-10-01", "1993-01-01", "1993-04-01", "1993-07-01", 
"1993-10-01", "1994-01-01", "1994-04-01", "1994-07-01", "1994-10-01", 
"1995-01-01", "1995-04-01", "1995-07-01", "1995-10-01", "1996-01-01", 
"1996-04-01", "1996-07-01", "1996-10-01", "1997-01-01", "1997-04-01", 
"1997-07-01", "1997-10-01", "1998-01-01", "1998-04-01", "1998-07-01", 
"1998-10-01", "1999-01-01", "1999-04-01", "1999-07-01", "1999-10-01", 
"2000-01-01", "2000-04-01", "2000-07-01", "2000-10-01", "2001-01-01", 
"2001-04-01", "2001-07-01", "2001-10-01", "2002-01-01", "2002-04-01", 
"2002-07-01", "2002-10-01", "2003-01-01", "2003-04-01", "2003-07-01", 
"2003-10-01", "2004-01-01", "2004-04-01", "2004-07-01", "2004-10-01", 
"2005-01-01", "2005-04-01", "2005-07-01", "2005-10-01", "2006-01-01", 
"2006-04-01", "2006-07-01", "2006-10-01", "2007-01-01", "2007-04-01", 
"2007-07-01", "2007-10-01", "2008-01-01", "2008-04-01", "2008-07-01", 
"2008-10-01", "2009-01-01", "2009-04-01", "2009-07-01", "2009-10-01", 
"2010-01-01", "2010-04-01", "2010-07-01", "2010-10-01", "2011-01-01", 
"2011-04-01", "2011-07-01", "2011-10-01", "2012-01-01", "2012-04-01", 
"2012-07-01", "2012-10-01", "2013-01-01", "2013-04-01", "2013-07-01", 
"2013-10-01", "2014-01-01", "2014-04-01", "2014-07-01", "2014-10-01", 
"2015-01-01", "2015-04-01", "2015-07-01", "2015-10-01", "2016-01-01", 
"2016-04-01", "2016-07-01", "2016-10-01", "2017-01-01", "2017-04-01", 
"2017-07-01", "2017-10-01", "2018-01-01", "2018-04-01", "2018-07-01", 
"2018-10-01", "2019-01-01", "2019-04-01", "2019-07-01", "2019-10-01", 
"2020-01-01", "2020-04-01", "2020-07-01", "2020-10-01", "2021-01-01", 
"2021-04-01", "2021-07-01", "2021-10-01", "2022-01-01", "1996-01-01", 
"1996-04-01", "1996-07-01", "1996-10-01", "1997-01-01", "1997-04-01", 
"1997-07-01", "1997-10-01", "1998-01-01", "1998-04-01", "1998-07-01", 
"1998-10-01", "1999-01-01", "1999-04-01", "1999-07-01", "1999-10-01", 
"2000-01-01", "2000-04-01", "2000-07-01", "2000-10-01", "2001-01-01", 
"2001-04-01", "2001-07-01", "2001-10-01", "2002-01-01", "2002-04-01", 
"2002-07-01", "2002-10-01", "2003-01-01", "2003-04-01", "2003-07-01", 
"2003-10-01", "2004-01-01", "2004-04-01", "2004-07-01", "2004-10-01", 
"2005-01-01", "2005-04-01", "2005-07-01", "2005-10-01", "2006-01-01", 
"2006-04-01", "2006-07-01", "2006-10-01", "2007-01-01", "2007-04-01", 
"2007-07-01", "2007-10-01", "2008-01-01", "2008-04-01", "2008-07-01", 
"2008-10-01", "2009-01-01", "2009-04-01", "2009-07-01", "2009-10-01", 
"2010-01-01", "2010-04-01", "2010-07-01", "2010-10-01", "2011-01-01", 
"2011-04-01", "2011-07-01", "2011-10-01", "2012-01-01", "2012-04-01", 
"2012-07-01", "2012-10-01", "2013-01-01", "2013-04-01", "2013-07-01", 
"2013-10-01", "2014-01-01", "2014-04-01", "2014-07-01", "2014-10-01", 
"2015-01-01", "2015-04-01", "2015-07-01", "2015-10-01", "2016-01-01", 
"2016-04-01", "2016-07-01", "2016-10-01", "2017-01-01", "2017-04-01", 
"2017-07-01", "2017-10-01", "2018-01-01", "2018-04-01", "2018-07-01", 
"2018-10-01", "2019-01-01", "2019-04-01", "2019-07-01", "2019-10-01", 
"2020-01-01", "2020-04-01", "2020-07-01", "2020-10-01", "2021-01-01", 
"2021-04-01", "2021-07-01", "2021-10-01", "2022-01-01", "2022-04-01", 
"2022-07-01", "2022-10-01", "2023-01-01", "2023-04-01", "2023-07-01", 
"2023-10-01", "2024-01-01", "2024-04-01", "2024-07-01", "2024-10-01", 
"2025-01-01", "1979-01-01", "1979-04-01", "1979-07-01", "1979-10-01", 
"1980-01-01", "1980-04-01", "1980-07-01", "1980-10-01", "1981-01-01", 
"1981-04-01", "1981-07-01", "1981-10-01", "1982-01-01", "1982-04-01", 
"1982-07-01", "1982-10-01", "1983-01-01", "1983-04-01", "1983-07-01", 
"1983-10-01", "1984-01-01", "1984-04-01", "1984-07-01", "1984-10-01", 
"1985-01-01", "1985-04-01", "1985-07-01", "1985-10-01", "1986-01-01", 
"1986-04-01", "1986-07-01", "1986-10-01", "1987-01-01", "1987-04-01", 
"1987-07-01", "1987-10-01", "1988-01-01", "1988-04-01", "1988-07-01", 
"1988-10-01", "1989-01-01", "1989-04-01", "1989-07-01", "1989-10-01", 
"1990-01-01", "1990-04-01", "1990-07-01", "1990-10-01", "1991-01-01", 
"1991-04-01", "1991-07-01", "1991-10-01", "1992-01-01", "1992-04-01", 
"1992-07-01", "1992-10-01", "1993-01-01", "1993-04-01", "1993-07-01", 
"1993-10-01", "1994-01-01", "1994-04-01", "1994-07-01", "1994-10-01", 
"1995-01-01", "1995-04-01", "1995-07-01", "1995-10-01", "1996-01-01", 
"1996-04-01", "1996-07-01", "1996-10-01", "1997-01-01", "1997-04-01", 
"1997-07-01", "1997-10-01", "1998-01-01", "1998-04-01", "1998-07-01", 
"1998-10-01", "1999-01-01", "1999-04-01", "1999-07-01", "1999-10-01", 
"2000-01-01", "2000-04-01", "2000-07-01", "2000-10-01", "2001-01-01", 
"2001-04-01", "2001-07-01", "2001-10-01", "2002-01-01", "2002-04-01", 
"2002-07-01", "2002-10-01", "2003-01-01", "2003-04-01", "2003-07-01", 
"2003-10-01", "2004-01-01", "2004-04-01", "2004-07-01", "2004-10-01", 
"2005-01-01", "2005-04-01", "2005-07-01", "2005-10-01", "2006-01-01", 
"2006-04-01", "2006-07-01", "2006-10-01", "2007-01-01", "2007-04-01", 
"2007-07-01", "2007-10-01", "2008-01-01", "2008-04-01", "2008-07-01", 
"2008-10-01", "2009-01-01", "2009-04-01", "2009-07-01", "2009-10-01", 
"2010-01-01", "2010-04-01", "2010-07-01", "2010-10-01", "2011-01-01", 
"2011-04-01", "2011-07-01", "2011-10-01", "2012-01-01", "2012-04-01", 
"2012-07-01", "2012-10-01", "2013-01-01", "2013-04-01", "2013-07-01", 
"2013-10-01", "2014-01-01", "2014-04-01", "2014-07-01", "2014-10-01", 
"2015-01-01", "2015-04-01", "2015-07-01", "2015-10-01", "2016-01-01", 
"2016-04-01", "2016-07-01", "2016-10-01", "2017-01-01", "2017-04-01", 
"2017-07-01", "2017-10-01", "2018-01-01", "2018-04-01", "2018-07-01", 
"2018-10-01", "2019-01-01", "2019-04-01", "2019-07-01", "2019-10-01", 
"2020-01-01", "2020-04-01", "2020-07-01", "2020-10-01", "2021-01-01", 
"2021-04-01", "2021-07-01", "2021-10-01", "2022-01-01", "2022-04-01", 
"2022-07-01", "2022-10-01", "2023-01-01", "2023-04-01", "2023-07-01", 
"2023-10-01", "2024-01-01", "2024-04-01", "2024-07-01", "2024-10-01", 
"1970-01-01", "1970-04-01", "1970-07-01", "1970-10-01", "1971-01-01", 
"1971-04-01", "1971-07-01", "1971-10-01", "1972-01-01", "1972-04-01", 
"1972-07-01", "1972-10-01", "1973-01-01", "1973-04-01", "1973-07-01", 
"1973-10-01", "1974-01-01", "1974-04-01", "1974-07-01", "1974-10-01", 
"1975-01-01", "1975-04-01", "1975-07-01", "1975-10-01", "1976-01-01", 
"1976-04-01", "1976-07-01", "1976-10-01", "1977-01-01", "1977-04-01", 
"1977-07-01", "1977-10-01", "1978-01-01", "1978-04-01", "1978-07-01", 
"1978-10-01", "1979-01-01", "1979-04-01", "1979-07-01", "1979-10-01", 
"1980-01-01", "1980-04-01", "1980-07-01", "1980-10-01", "1981-01-01", 
"1981-04-01", "1981-07-01", "1981-10-01", "1982-01-01", "1982-04-01", 
"1982-07-01", "1982-10-01", "1983-01-01", "1983-04-01", "1983-07-01", 
"1983-10-01", "1984-01-01", "1984-04-01", "1984-07-01", "1984-10-01", 
"1985-01-01", "1985-04-01", "1985-07-01", "1985-10-01", "1986-01-01", 
"1986-04-01", "1986-07-01", "1986-10-01", "1987-01-01", "1987-04-01", 
"1987-07-01", "1987-10-01", "1988-01-01", "1988-04-01", "1988-07-01", 
"1988-10-01", "1989-01-01", "1989-04-01", "1989-07-01", "1989-10-01", 
"1990-01-01", "1990-04-01", "1990-07-01", "1990-10-01", "1991-01-01", 
"1991-04-01", "1991-07-01", "1991-10-01", "1992-01-01", "1992-04-01", 
"1992-07-01", "1992-10-01", "1993-01-01", "1993-04-01", "1993-07-01", 
"1993-10-01", "1994-01-01", "1994-04-01", "1994-07-01", "1994-10-01", 
"1995-01-01", "1995-04-01", "1995-07-01", "1995-10-01", "1996-01-01", 
"1996-04-01", "1996-07-01", "1996-10-01", "1997-01-01", "1997-04-01", 
"1997-07-01", "1997-10-01", "1998-01-01", "1998-04-01", "1998-07-01", 
"1998-10-01", "1999-01-01", "1999-04-01", "1999-07-01", "1999-10-01", 
"2000-01-01", "2000-04-01", "2000-07-01", "2000-10-01", "2001-01-01", 
"2001-04-01", "2001-07-01", "2001-10-01", "2002-01-01", "2002-04-01", 
"2002-07-01", "2002-10-01", "2003-01-01", "2003-04-01", "2003-07-01", 
"2003-10-01", "2004-01-01", "2004-04-01", "2004-07-01", "2004-10-01", 
"2005-01-01", "2005-04-01", "2005-07-01", "2005-10-01", "2006-01-01", 
"2006-04-01", "2006-07-01", "2006-10-01", "2007-01-01", "2007-04-01", 
"2007-07-01", "2007-10-01", "2008-01-01", "2008-04-01", "2008-07-01", 
"2008-10-01", "2009-01-01", "2009-04-01", "2009-07-01", "2009-10-01", 
"2010-01-01", "2010-04-01", "2010-07-01", "2010-10-01", "2011-01-01", 
"2011-04-01", "2011-07-01", "2011-10-01", "2012-01-01", "2012-04-01", 
"2012-07-01", "2012-10-01", "2013-01-01", "2013-04-01", "2013-07-01", 
"2013-10-01", "2014-01-01", "2014-04-01", "2014-07-01", "2014-10-01", 
"2015-01-01", "2015-04-01", "2015-07-01", "2015-10-01", "2016-01-01", 
"2016-04-01", "2016-07-01", "2016-10-01", "2017-01-01", "2017-04-01", 
"2017-07-01", "2017-10-01", "2018-01-01", "2018-04-01", "2018-07-01", 
"2018-10-01", "2019-01-01", "2019-04-01", "2019-07-01", "2019-10-01", 
"2020-01-01", "2020-04-01", "2020-07-01", "2020-10-01", "2021-01-01", 
"2021-04-01", "2021-07-01", "2021-10-01", "2022-01-01", "2022-04-01", 
"2022-07-01", "2022-10-01", "2023-01-01", "2023-04-01", "2023-07-01", 
"2023-10-01"), na_item = c("GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", 
"GValueAdd", "GValueAdd", "GValueAdd", "GValueAdd", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Export", "Export", "Export", "Export", 
"Export", "Export", "Export", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"Import", "Import", "Import", "Import", "Import", "Import", "Import", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "GCapitalForm", "GCapitalForm", "GCapitalForm", 
"GCapitalForm", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpGov", "FinConsExpGov", 
"FinConsExpGov", "FinConsExpGov", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "FinConsExpHH", 
"FinConsExpHH", "FinConsExpHH", "FinConsExpHH", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", 
"StatDiscrep", "StatDiscrep", "StatDiscrep", "StatDiscrep", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", "HICP_Energy", 
"HICP_Energy", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "HDD", 
"HDD", "HDD", "HDD", "HDD", "HDD", "HDD", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion", 
"EmiCO2Combustion", "EmiCO2Combustion", "EmiCO2Combustion"), 
    values = c(437661.5, 433434.7, 432813.1, 439029, 445851.8, 
    442867.8, 441935.4, 439759.6, 436900.1, 436465, 437894.8, 
    437832.6, 441345.1, 445696.4, 448369.3, 454088.1, 451819.2, 
    456046.5, 457165.5, 458284.4, 451493, 460133.7, 460382.4, 
    466660.9, 462714, 468619.1, 470608.2, 476264.7, 479186.8, 
    476886.6, 479373.3, 480554.5, 483989, 483864.7, 489956.6, 
    492007.9, 500306.7, 504161, 506274.6, 504596.1, 515583.5, 
    513221.3, 514588.9, 514091.6, 512040.2, 514215.9, 516080.8, 
    517137.6, 508932, 508807.7, 515024.1, 515583.5, 514604.3, 
    520199.3, 517526.1, 517526.1, 518691.7, 520991.7, 524472.9, 
    527829.7, 533315.3, 542577.9, 547737.7, 555135.3, 556751.1, 
    562408.1, 565081.2, 569867.9, 572898.2, 571654.9, 567614.3, 
    557357.3, 528948.7, 530067.6, 533362.2, 537402.9, 545904, 
    554855.3, 560139, 563495.8, 574701, 575757.7, 579611.9, 579611.9, 
    580761.8, 581943, 582937.7, 580513.2, 578430.8, 584211.9, 
    587257.9, 589993.1, 596644.6, 594531.1, 598136.5, 602674.5, 
    600374.5, 604539.4, 606590.8, 608144.9, 615790.9, 618277.5, 
    619209.9, 621883, 629218.3, 635186, 641464.5, 646934.8, 644494.9, 
    647603.1, 643624.7, 648038.2, 650540.3, 649794.4, 651534.9, 
    651161.9, 640221.2, 578492.9, 628348, 633880.5, 628922.6, 
    642225.9, 649810.1, 652856.1, 654223.5, 651985.5, 657518.2, 
    657145.2, 656850, 655979.7, 656477, 663066, 659756.1, 657704.7, 
    655218.1, 653477.5, 657207.3, 101231.1, 95359.5, 100001.5, 
    100155.2, 101407.7, 96489.5, 99225.3, 94614.4, 91363.9, 89334.9, 
    89611.6, 91240.9, 94276.3, 98610.5, 98210.9, 98764.2, 102760.2, 
    103528.7, 104266.4, 105895.6, 107470.8, 107778.2, 110514.1, 
    115402, 117569.1, 120980.9, 127466.4, 129157, 132077.5, 134136.9, 
    132753.7, 130479.2, 131278.7, 138071.6, 141114.6, 144003.9, 
    150874, 156315, 158989.4, 167289.4, 166966.2, 167458, 167119.9, 
    169179.3, 168449.3, 173521.2, 176287.7, 179453.8, 174043.8, 
    173306.1, 178439.5, 182742.9, 190127.8, 198427.6, 194861.7, 
    195876.2, 200725.2, 204260.2, 212344.5, 215572.1, 222557.1, 
    229412.1, 235683.1, 249208.7, 247463.3, 253672.9, 258407, 
    260743.3, 263078.8, 261972.2, 259421.1, 244820.9, 216432.8, 
    214649.9, 221320.3, 227683.2, 234668.2, 251267.7, 255110.2, 
    260059.3, 266721.7, 270348.8, 273084.6, 271639.9, 277295.9, 
    279416.8, 282583, 277726.2, 276888.7, 277780.1, 282483, 287124.5, 
    287055.8, 289668.5, 294832.3, 300303.6, 302148.1, 307343.3, 
    307312.5, 305560.3, 308741.8, 311969.4, 311385.4, 312399.7, 
    319561.9, 325002.7, 328322.5, 330812.3, 335699.8, 336222.4, 
    333025.5, 333486.6, 343538.3, 338281.9, 342093.5, 340157, 
    331550.1, 261895.7, 308280.7, 322451.4, 332326.2, 334570.1, 
    331465.4, 345790.1, 343353.8, 343999.3, 349378.6, 350454.5, 
    350247.1, 348986.8, 346650.5, 344037.7, 344222.3, 350523.9, 
    341394.2, 330727.6, 341425, 95272.2, 95907, 97149, 96928.2, 
    100295.4, 97507.9, 97038.7, 98418.7, 89013.6, 89758.8, 91028.5, 
    91194.1, 93077.6, 97107.6, 99039.8, 100916.8, 101358, 104118.3, 
    104891.2, 106050.5, 106402.3, 107119.9, 107865.2, 112005.3, 
    115283.2, 116442.3, 120278.7, 121851.9, 126461.6, 129442.3, 
    130215.1, 129663.1, 134941.9, 139192.5, 142615, 142780.6, 
    147638.4, 151944.2, 156884.8, 165027.1, 158727.1, 159141.1, 
    156022.3, 154035.1, 148687.2, 151916.6, 152165, 155808.3, 
    159072.2, 157333.2, 158575.3, 163378.1, 164806.3, 168173.6, 
    171458.2, 172037.8, 169271.2, 177772, 182436.4, 189336.4, 
    193891.2, 196844.4, 200460, 206890.9, 208857.7, 209934.1, 
    214543.5, 214653.9, 216068.5, 213805.2, 217779.9, 210520.5, 
    197548.3, 187556.3, 194015.2, 192331.5, 204959.4, 219808.3, 
    219201.1, 221905.9, 227550.4, 233208.8, 233181.2, 230917.9, 
    230835.1, 231607.9, 232298, 230448.6, 230979.7, 234926.9, 
    238460, 238515.2, 238936.2, 242910.6, 244345.8, 248734.3, 
    253178.2, 253785.5, 256269.5, 259167.5, 263783.9, 262376.3, 
    263866.7, 269635.3, 270518.6, 277474.1, 277722.5, 281862.7, 
    286306.4, 287686.5, 294310.8, 296215.2, 300838.4, 297967.7, 
    302356.5, 304316.3, 299085.7, 246146.8, 272450.7, 282387.1, 
    292185.5, 294090, 296242.8, 314984, 313024.3, 319096.6, 324920.4, 
    325941.7, 322629.5, 324147.6, 319731.4, 313217.5, 312279.1, 
    320890.6, 320614.6, 318434.1, 321856.7, 120898.5, 125156.5, 
    122388.8, 123652, 125621.2, 124826.4, 117375.1, 120696.3, 
    110708.5, 115972.9, 118158.1, 114312.7, 116530.3, 117410.3, 
    121597.5, 126139.5, 121835.2, 124007.3, 122388.9, 119705.7, 
    114699.7, 119638.6, 117396.2, 120334, 117744, 119787.8, 119518.1, 
    122910.2, 124684.6, 123577.6, 125947.8, 125252.3, 128485.2, 
    124395.5, 131197.4, 128215.4, 129723.1, 130432.9, 133300.8, 
    130063.8, 132225.3, 133176.3, 129343.7, 120826.8, 116115.1, 
    118158.7, 116682.8, 112893.7, 115941.5, 115359.5, 113230, 
    113641.7, 108195.5, 107003.6, 112324.7, 111161.1, 102336.6, 
    107744.4, 109334.1, 115323.9, 115870.5, 120511.6, 121760.6, 
    119731, 128307.5, 124461.1, 127881.7, 129726.9, 129859.2, 
    125598.7, 129092.3, 127601.2, 109547, 100803.7, 104494.1, 
    101002.4, 111240.9, 120152.7, 118889.7, 118832.9, 129812.1, 
    131543.7, 130919.2, 128463.7, 122562.7, 120859.4, 118389.7, 
    120334.2, 118181.7, 125991.4, 125892, 124486.2, 129833, 129606, 
    125859.6, 126895.5, 125830.7, 123318.9, 125362.4, 127349.1, 
    131203, 128804.6, 130677.9, 133289.2, 135204.9, 138782.4, 
    140769.8, 143467.1, 140407.1, 144282.4, 148470.1, 148711.4, 
    145088, 146266.2, 144662.2, 146379.8, 147804.5, 140156.1, 
    134054.3, 143575.9, 149605.3, 152117.6, 141074.6, 145829.7, 
    141927.2, 145361.5, 148526.1, 150583.9, 149214.5, 147468.8, 
    146078, 140160, 140500.4, 137875.1, 143310.1, 147595.6, 142884.4, 
    81887.8, 83172.2, 85493.2, 86313.4, 87949.8, 88847.2, 90162.5, 
    90348.1, 90711.8, 90309.5, 90092.8, 89953.6, 92661.5, 93326.9, 
    93373.3, 94549.4, 93415.9, 95087.1, 96557.1, 97980.7, 96932.3, 
    97984.5, 99439.1, 99377.2, 99620.9, 100255.3, 100317.2, 98537.7, 
    102205, 102700.2, 102731.1, 102390.7, 105675.1, 105009.7, 
    105706, 104963.3, 107884, 107342.4, 106971, 107791.1, 107972.9, 
    107586.1, 107183.8, 108777.5, 108522.2, 108909.1, 109265, 
    110766, 109245.7, 109400.4, 110468.1, 111179.9, 109559, 109357.8, 
    110147, 108769.8, 109060, 110622.8, 110313.4, 110328.8, 111005.8, 
    110959.4, 111748.5, 112058, 112986.5, 113450.7, 113373.3, 
    114286.2, 116255.3, 118530, 117787.2, 118762.1, 120344.3, 
    121210.8, 122046.5, 121891.7, 123311.4, 122321.1, 123698.3, 
    124007.7, 123884, 124472, 124564.8, 125292.1, 125400.4, 125942, 
    126483.6, 126762.1, 127829.8, 127613.2, 128619, 128665.4, 
    129237.9, 129934.2, 130893.6, 131822.1, 132429.4, 133203.1, 
    134456.5, 136777.7, 138212.8, 139404.3, 139791.1, 140982.6, 
    140669.3, 141396.5, 141767.9, 143423.6, 142495.2, 143377.2, 
    143067.7, 144181.8, 146089, 146460.4, 148611.2, 148719.6, 
    151752.4, 151566.8, 158096.7, 157539.7, 157094.7, 161551.3, 
    160947.8, 160468.1, 162027.1, 161980.7, 158344.3, 158545.5, 
    159551.3, 158870.4, 160108.3, 161470.1, 162197.3, 164595.8, 
    166514.5, 167241.8, 166669.3, 280780, 280419.8, 275881.2, 
    280167.7, 286102.1, 285273.6, 286570.3, 288587.4, 287434.8, 
    285669.9, 287578.9, 289848.1, 290289.5, 291262, 292378.7, 
    293567.3, 293324.1, 295629.5, 296710.2, 297754.8, 299105.5, 
    300474.3, 300942.5, 301879, 302968.7, 303761.1, 302968.7, 
    305202, 306687.8, 305787.2, 308092.6, 310938.3, 315359.8, 
    316836.6, 316728.5, 320474.7, 322554.9, 325544.5, 325544.5, 
    325184.3, 329020.6, 326607.1, 327975.9, 329128.6, 326679.2, 
    324301.8, 326715.2, 328120.1, 327705.8, 327813.9, 330047.1, 
    330083.1, 330263.2, 329795, 328822.5, 330587.4, 332550.5, 
    333667.2, 333631.2, 333487.1, 336422.8, 338007.7, 338007.7, 
    341501.6, 336602.9, 338944.2, 338620, 338223.8, 339124.3, 
    337791.5, 338007.6, 336134.6, 338881.2, 340105.8, 338989.2, 
    339313.4, 337287.3, 340421.1, 342077.9, 343734.8, 343023.5, 
    344356.3, 345689, 346697.6, 348426.6, 349002.9, 350047.5, 
    348498.6, 347490.1, 350443.7, 351740.5, 349399.1, 350596.8, 
    351785.5, 354487.1, 356468.2, 357981, 359565.9, 361691.2, 
    364861.1, 367229.3, 366436.9, 368129.8, 371371.7, 372101, 
    374982.7, 374658.5, 378476.8, 378611.8, 379692.4, 379332.2, 
    383798.8, 384663.3, 385779.9, 387797, 389129.8, 371453, 332189.7, 
    370336.4, 364681, 350219, 360880.9, 378458.5, 381664.2, 386797.4, 
    387806, 392740.9, 386365.2, 384915.4, 389273.9, 388949.7, 
    387689, 387400.8, 387761, 388805.6, 389742.1, 391651.2, 0, 
    0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
    0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
    0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
    0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
    0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
    0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
    0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 151.9, 153.2, 153.7, 157.5, 
    158.6, 157, 158.7, 159, 154.7, 154.1, 153.1, 151, 149.4, 
    159, 164, 166, 173.5, 176.9, 186, 190.5, 190.9, 197.4, 193.8, 
    186.4, 190, 194.4, 193.5, 192.8, 204.3, 198.1, 199.4, 199.1, 
    201.1, 208, 211.7, 213.2, 214.7, 225.4, 239.1, 240.7, 244.6, 
    254, 253.9, 245, 250.5, 258.5, 260.8, 266.1, 274.1, 289.3, 
    294.9, 274.8, 268.1, 269.1, 268.1, 266.7, 272.6, 280.5, 278.4, 
    282.9, 299, 307.5, 307.8, 311.3, 320.3, 322.3, 326.7, 324.6, 
    330.4, 328.9, 331.8, 326.1, 323.9, 326.3, 325.6, 314.2, 300.5, 
    308.4, 300.9, 290.3, 277.2, 284.8, 284.3, 288.7, 294.1, 291.3, 
    289.7, 294.6, 295.3, 303.8, 310.5, 317.6, 305.6, 315.4, 312.3, 
    311.1, 310.4, 294.7, 292.5, 290.4, 312.9, 320.4, 328.5, 346.3, 
    397.2, 437.2, 455.2, 471.9, 464.7, 463.8, 467.7, 454.7, 451.6, 
    456.4, 445, 438.7, 443.7, 1680.89, 547.63, 230.25, 1120, 
    1526.24, 650.83, 194.07, 1272.41, 1443.18, 498.35, 171.77, 
    1313.31, 1529.73, 544.51, 68.44, 1072.23, 1375.8, 501.82, 
    120.24, 1217.61, 1515.18, 639.95, 231.48, 1118.72, 1766.87, 
    534.83, 154.75, 1208.77, 1682.82, 513.07, 279.58, 1081.53, 
    1805.8, 606.37, 168.64, 1121.85, 1348.45, 452.73, 153.44, 
    1134.73, 1197.54, 504.23, 147.42, 1135.85, 1127.19, 481.35, 
    210.54, 1138.5, 1409.78, 684.11, 79.72, 1229.47, 1345.05, 
    423.28, 113.61, 1224.49, 1423.18, 358.91, 244.86, 1270.96, 
    1308.78, 502.84, 135.55, 1057.29, 1351.34, 548.51, 152.69, 
    1211.96, 1729.44, 564.76, 260.03, 1268.06, 1375.15, 555, 
    112.22, 1186.04, 1239.37, 417.06, 190.87, 1287.88, 1336.13, 
    450.3, 43.1, 1174.1, 1306.52, 371.38, 151.82, 1012.55, 1376.65, 
    518.72, 187.96, 1133.41, 1259.94, 441.43, 141.08, 1210.53, 
    1495.64, 399.81, 113.27, 1213.12, 1409.86, 492.02, 134.15, 
    1138.1, 1435.61, 476.69, 124.67, 1112.09, 1628.71, 467.55, 
    49.51, 878.27, 1132.88, 311.62, 179.27, 1196.61, 1241.69, 
    431.69, 169.45, 1143.01, 1503.68, 360.51, 80.54, 1136.65, 
    1584.22, 535.98, 169.73, 1345.47, 1379.42, 319.26, 119.25, 
    1055.09, 1398.72, 456.36, 131.12, 1144.73, 1602.13, 519.26, 
    134.47, 1033.2, 1177.58, 404.89, 116.04, 960.49, 1337.65, 
    494.33, 144.73, 931.71, 1352.24, 421.56, 61.32, 1173.9, 1348.93, 
    435.13, 148.65, 1033.12, 1448.44, 235.06, 87.83, 1003.62, 
    1242.92, 444.15, 106.72, 1007.02, 1184.19, 435.96, 100.6, 
    1020.28, 1368.49, 565.71, 83.38, 1096.61, 1218.79, 418.1, 
    122.68, 977.14, 1202.4, 452.49, 45.8, 961.19, 1133.76, 322.59, 
    83.66, 1028.74, 315959.2508, 217938.6763, 182441.9371, 270439.704, 
    311759.4265, 214597.1071, 184555.2462, 271927.9195, 306081.8865, 
    223257.973, 193654.1412, 283424.4236, 323183.368, 235987.2834, 
    195154.2959, 303009.4951, 306492.2935, 234539.8137, 198693.9638, 
    291409.3072, 294323.2906, 222231.9152, 178630.9187, 283529.9879, 
    322394.7015, 226876.1586, 194527.6614, 291155.4936, 307274.0779, 
    231835.317, 197407.8412, 282462.9079, 318807.5533, 234927.2836, 
    205374.0388, 292597.7072, 348353.3223, 240950.3723, 210818.626, 
    298926.8432, 319043.1442, 236024.4551, 200796.662, 292286.4314, 
    307203.8184, 223172.4507, 195139.6548, 290351.0165, 305063.7118, 
    218884.1473, 183004.5915, 267574.6962, 294605.8292, 217781.1306, 
    186714.8774, 276978.0405, 303492.6226, 225741.947, 195175.6009, 
    271269.7972, 318690.7306, 219555.0137, 190127.4258, 275882.9277, 
    319436.1183, 219503.4338, 196293.3967, 271726.3952, 319204.411, 
    220795.7212, 188895.5353, 268237.778, 300700.395, 218401.7577, 
    192479.0497, 278039.2445, 283562.6126, 219310.5227, 190556.6878, 
    272367.9501, 271850.7956, 211509.4419, 189257.06, 267390.3866, 
    273551.8172, 211930.7975, 175103.9506, 257057.5971, 262365.0602, 
    193306.9517, 171402.0331, 250527.4965, 260796.1747, 187206.6246, 
    176142.4951, 247676.6093, 257625.5944, 194652.4497, 168689.1085, 
    238139.2397, 253492.2694, 192997.0441, 168015.9787, 242091.6229, 
    273396.4302, 194104.9563, 175446.5356, 244114.1796, 255746.1296, 
    192750.4797, 164933.444, 241489.6615, 246496.2198, 185508.2922, 
    169959.6438, 244979.6987, 243344.2561, 182050.6226, 158533.349, 
    231031.1456, 243785.3149, 179303.5753, 165110.2274, 224112.4915, 
    247401.3228, 188362.7824, 160292.351, 235422.7621, 237357.0563, 
    183934.9094, 161796.7479, 234813.1866, 246652.0347, 179337.4731, 
    164150.0575, 230548.8317, 238813.7467, 180122.9598, 162121.4667, 
    223566.7427, 231799.6998, 179357.7425, 155448.6487, 220325.4836, 
    258774.4482, 176522.7093, 152560.4805, 210824.2183, 211077.7689, 
    170206.7548, 162134.306, 223600.6134, 222646.1092, 177770.6169, 
    156822.3736, 216654.0862, 218341.5393, 152801.6933, 145587.059, 
    203451.8674, 225069.9528, 170428.4186, 147378.0532, 215971.9513, 
    215632.7025, 162571.0888, 148629.7802, 204408.0237, 220430.2187, 
    167934.4471, 149894.7885, 206882.1391, 236369.8544, 170694.6265, 
    153672.1944, 202915.136, 210385.3333, 162823.9862, 148055.6526, 
    201846.7588, 217726.7331, 161357.7723, 151347.5264, 199252.3698, 
    213279.9471, 161908.3333, 147096.4864, 212202.3868, 214263.5152, 
    163534.2815, 149488.2187, 191508.1581, 214806.0654, 151468.6977, 
    141726.7265, 186538.6611, 192040.381, 147227.9541, 131162.9058, 
    174972.2707, 176183.1695, 134711.7834, 118426.7956, 163774.9534, 
    186227.25, 144225.2657, 124876.3903, 168760.4006, 182956.5457, 
    139386.7467, 124839.515, 166549.9458, 161156.3995, 121920.9554, 
    108013.8317, 147474.1009)), class = c("tbl_df", "tbl", "data.frame"
), row.names = c(NA, -1464L))

```



```{r run-model, eval = FALSE}
model <- run_model(specification = specification,
                   dictionary = dict,
                   inputdata_directory = NULL,
                   primary_source = "local",
                   save_to_disk = "./Downloaded_Input.xlsx",
                   present = FALSE,
                   quiet = FALSE, 
                   plot = FALSE)
class(model)
```


```{r run-model-true, include = FALSE}
model <- run_model(specification = specification,
                   dictionary = dict,
                   inputdata_directory = dat,
                   primary_source = "local",
                   present = FALSE,
                   quiet = FALSE, 
                   plot = FALSE)
class(model)
```

```{r, fig.width=7, fig.height=5}
plot(model)
```


We did not `quiet` the output, so we get some information about the estimation.

We are told that local files are used, namely the file 
`"example-workflow-data.rds"`, which can be found in our working directory 
`"."` from where the vignette is created. Next, we obtain a warning that the 
panel is unbalanced, which means that we have "ragged edges" that cause more
than 20\% of the data to be discarded when limiting the sample to the time
periods that are available for **all** variables.

Finally, the estimation begins. The order of the modules is determined by how
they are related to each other, starting with the modules that only depend on
exogenous (unmodelled) variables and then gradually estimating the other modules
in order to avoid any reverse dependencies.

# Evaluating the Model

Now, we can have a look at the model results.

## Individual Module Results

The different modules are stored in `model$module_collection`, which is a tibble
that stores the datasets, independent and dependent variables, model arguments,
and the model itself as an `"isat"` object.

For example, taking a closer look at the estimated module for carbon emissions
from combustion activities:

```{r module emissions}
# extract the isat model object
co2module <- model$module_collection %>% 
  filter(dependent == "EmiCO2Combustion") %>% 
  pull(model) %>% 
  pluck(1)
class(co2module)
# inspect the estimated equation
print(co2module)
```
We find that the number of heating degree days (`HDD`) and gross value added
(`GValueAdd`) are significant, while gets model selection dropped the harmonised
consumer price index for energy. Both gross value added and heating degree days
have a positive coefficient meaning that they increase emissions, as we would
expect.

Both diagnostic tests of no autocorrelation and no autoregressive conditional
heteroskedasticity pass.

## Module Network

We can show the relationship between the different modules using the `network()`
function.

```{r network, fig.width=7, fig.height=5}
network(model)
```
Each node represents a module and the different colours represent whether the
variable is given by a definition/identity, whether it has been modelled as an
endogenous variable depending on other models, and whether it is an exogenous
variable input to the models.

An solid line arrow means that the variable has been retained during model
selection, while a dashed arrow means that the variable has been dropped during
model selection. Note again that `HICP_Energy` was in the original specification
but has been found to be insignificant.

## Forecasts

We can use our model to forecast the variables of our modules. This works for
both the definition/identity modules and the endogenous modules. The user can
either provide future values for the exogenous variables (e.g. corresponding to
certain scenario assumptions) or use automatic AR models to forecast future
values of the exogenous variables.

```{r, forecast}
forecast <- forecast_model(model = model,
                           exog_predictions = NULL,
                           plot = FALSE)
class(forecast)
```
We did not specify paths for the exogenous regressors, so the output informs us
that AR(4) processes were used to project their paths. The function returns an
object of class `"osem.forecast"`, which can also be plotted.

```{r, forecast-plot, fig.width=7, fig.height=5}
plot(forecast)
```

## Diagnostics

To obtain an overview of the diagnostic results for each endogenous module, we
can use the command `diagnostics_model()`. This avoids having to look at all
`"isat"` model objects manually.

```{r, diagnostics}
diagnostics_model(model)
```

The diagnostics pass for both modules: we neither have evidence for 
autocorrelated errors nor for autoregressive conditional heteroskedasticity.

The output also shows how many impulse indicators (representing outliers) and
step indicators (representing structural breaks of the mean) have been retained
in each module, both in absolute and as a share of the observations.

## Shiny App

Last but not least, we can get an overview and summary of the whole OSEM
model results in a Shiny app, which can be opened using the `present_model()`
command. The following code snippet is not executed:

```{r, shiny, eval=FALSE}
present_model(model)
```


