---
title: "Example Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
library(aggregate.model)
library(dplyr)
library(purrr)
```

# Setting up the Model

## Dictionary

In this illustration, we will rely on the default dictionary that is available
from `dict`.

```{r dictionary}
dict %>% 
  select(model_varname, database, dataset_id, variable_code, freq, geo) %>% 
  head()
dict %>% 
  select(model_varname, database, dataset_id, variable_code, freq, geo) %>% 
  tail()
```

## Specification

We use a specification for illustrative purposes only. Our specification
contains the following four modules/equations:

```{r specification}
specification <- dplyr::tibble(
    type = c(
      "d",
      "d",
      "n",
      "n"
    ),
    dependent = c(
      "StatDiscrep",
      "TOTS",
      "Import",
      "EmiCO2Combustion"
    ),
    independent = c(
      "TOTS - FinConsExpHH - FinConsExpGov - GCapitalForm - Export",
      "GValueAdd + Import",
      "FinConsExpHH + GCapitalForm",
      "HDD + HICP_Energy + GValueAdd"
    )
  )
print(specification)
```

The first two equations are simply accounting identities. The third equation
models imports as a function of final consumption expenditure of households and
gross capital formation. The fourth equation models carbon emissions from
combustion activities, which includes energy industries, manufacturing and 
construction, transport, and combustion activities in other sectors.The
regressors are the number of heating degree days, the harmonised
index of consumer prices for energy, and total gross value added.

## Data

We differentiate between where data can be obtained from *in principle* versus
where it should be obtained from *actually* in a specific model run. For 
example, a variable that is available on Eurostat can be downloaded from 
Eurostat but might have been saved locally from a previous model run. In order
to save time, the user might prefer that the local data is used rather than
re-downloading the data.

The dictionary specifies where the data for the different variables can be
obtained *in principle*. The column `dict$database` may take one of four
different values:

* `eurostat` if the variable is available from Eurostat using 
`eurostat::get_eurostat()`,
* `edgar` if the (emissions) variable is available EDGAR using a link,
* `local` if the variable is not available from the above two sources and is
therefore provided as a local file by the user in the directory 
`inputdata_directory`. This directory is searched for `.rds`, `.csv`,
and `.xlsx` files, opens them consecutively, and searches for the variable.
* `NA` if the variable is constructed as an identity/definition

The argument `primary_source` in the main function `run_model()` governs how the
data is *actually* obtained in this model run. Data that can in principle be
downloaded from `eurostat` or `edgar` can also be loaded locally if it has been
saved manually by the user or using the `save_to_disk` argument in `run_model()`
in a previous model run. The argument `primary_source` can take either the value
`"download"` or `"local"`, which governs whether download or local input takes
precedence for `eurostat` and `edgar` variables.

This gives rise to the following combinations of obtaining data:

* variables with `dictionary$database == "local"` are always searched for among
the local files of `inputdata_directory` and an error is raised if they cannot
be found there
* variables with `dictionary$database == "eurostat"` or 
`dictionary$database == "egdar"`
  * argument `primary_source == "download"` first downloads all the variables 
  (potentially updating the values) and only searches the local directory if 
  the variables cannot be obtained that way (e.g. if there were problems with 
  the download)
  * argument `primary_source == "local"` first searches the local directory and
  only downloads those variables that could not be found locally

Here, we use variables that can *in principle* all be obtained from either
Eurostat or EDGAR but we use the local file `example-workflow-data.rds` to save
time when compiling the vignette.

```{r dictionary$database}
vars <- c("StatDiscrep", "TOTS", "Import", "EmiCO2Combustion", "FinConsExpHH",
          "FinConsExpGov", "GCapitalForm", "Export", "GValueAdd", "HDD",
          "HICP_Energy")
dict %>% 
  filter(model_varname %in% vars) %>% 
  pull(database)
```
To avoid downloading all those variables again, we will specify 
`primary_source == "local"` and provide a `inputdata_directory` path to the
local directory when calling `run_model()`.

# Running the Model

We are now ready to run the model and obtain an `"aggmod"` object.

```{r run-model}
model <- run_model(specification = specification,
                   dictionary = dict,
                   inputdata_directory = ".",
                   primary_source = "local",
                   save_to_disk = NULL,
                   present = FALSE,
                   quiet = FALSE)
class(model)
```
We did not `quiet` the output, so we get some information about the estimation.

We are told that local files are used, namely the file 
`"example-workflow-data.rds"`, which can be found in our working directory 
`"."` from where the vignette is created. Next, we obtain a warning that the 
panel is unbalanced, which means that we have "ragged edges" that cause more
than 20\% of the data to be discarded when limiting the sample to the time
periods that are available for **all** variables.

Finally, the estimation begins. The order of the modules is determined by how
they are related to each other, starting with the modules that only depend on
exogenous (unmodelled) variables and then gradually estimating the other modules
in order to avoid any reverse dependencies.

# Evaluating the Model

Now, we can have a look at the model results.

## Individual Module Results

The different modules are stored in `model$module_collection`, which is a tibble
that stores the datasets, independent and dependent variables, model arguments,
and the model itself as an `"isat"` object.

For example, taking a closer look at the estimated module for carbon emissions
from combustion activities:

```{r module emissions}
# extract the isat model object
co2module <- model$module_collection %>% 
  filter(dependent == "EmiCO2Combustion") %>% 
  pull(model) %>% 
  pluck(1)
class(co2module)
# inspect the estimated equation
print(co2module)
```
We find that the number of heating degree days (`HDD`) and gross value added
(`GValueAdd`) are significant, while gets model selection dropped the harmonised
consumer price index for energy. Both gross value added and heating degree days
have a positive coefficient meaning that they increase emissions, as we would
expect.

Both diagnostic tests of no autocorrelation and no autoregressive conditional
heteroskedasticity pass.

## Module Network

We can show the relationship between the different modules using the `network()`
function.

```{r network, fig.width=7, fig.height=5}
network(model)
```
Each node represents a module and the different colours represent whether the
variable is given by a definition/identity, whether it has been modelled as an
endogenous variable depending on other models, and whether it is an exogenous
variable input to the models.

An solid line arrow means that the variable has been retained during model
selection, while a dashed arrow means that the variable has been dropped during
model selection. Note again that `HICP_Energy` was in the original specification
but has been found to be insignificant.

## Forecasts

We can use our model to forecast the variables of our modules. This works for
both the definition/identity modules and the endogenous modules. The user can
either provide future values for the exogenous variables (e.g. corresponding to
certain scenario assumptions) or use automatic AR models to forecast future
values of the exogenous variables.

```{r, forecast}
forecast <- forecast_model(model = model,
                           exog_predictions = NULL,
                           plot.forecast = FALSE)
class(forecast)
```
We did not specify paths for the exogenous regressors, so the output informs us
that AR(4) processes were used to project their paths. The function returns an
object of class `"aggmod.forecast"`, which can also be plotted.

```{r, forecast-plot, fig.width=7, fig.height=5}
plot(forecast)
```

## Diagnostics

To obtain an overview of the diagnostic results for each endogenous module, we
can use the command `diagnostics_model()`. This avoids having to look at all
`"isat"` model objects manually.

```{r, diagnostics}
diagnostics_model(model)
```

The diagnostics pass for both modules: we neither have evidence for 
autocorrelated errors nor for autoregressive conditional heteroskedasticity.

The output also shows how many impulse indicators (representing outliers) and
step indicators (representing structural breaks of the mean) have been retained
in each module, both in absolute and as a share of the observations.

## Shiny App

Last but not least, we can get an overview and summary of the whole aggregate
model results in a Shiny app, which can be opened using the `present_model()`
command. The following code snippet is not executed:

```{r, shiny, eval=FALSE}
present_model(model)
```


