---
title: "OSEM Illustration Germany"
author: "Jonas Kurle"
date: "`r Sys.Date()`"
output: 
  html_document:
    mathjax: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='hide'}
#devtools::install_github("moritzpschwarz/osem", ref = "main_nosuper")
#library(osem)
devtools::load_all()
library(tidyverse)
```

# Model Overview

We model the demand and the supply side separately.

$$
\begin{align}
\text{Supply} & = \text{GDPOutput} + \text{Imports} \\
\text{Demand} & = \text{GDPExpenditure} + \text{Imports} \\
\end{align}
$$
To model the supply side, $\text{GDPOutput}$ is first decomposed into its components.

$$
\begin{align}
\text{GDPOutput} & = \text{VA} + \text{Taxes} - \text{Subsidies}, \\
\end{align}
$$
where $\text{VA}$ is the sum of gross value added in different sectors. We decided to use the ISIC aggregation A*10/11. 

$$
\begin{align}
\text{VA} & = \text{VAAgriculture} + \text{VAIndustry} + \text{VAConstruction} + \text{VARetail} + \text{VAInformation} + \text{VAFinance} + \text{VARealEstate} + \text{VAService} + \text{VAGov} + \text{VAOther} \\
\end{align}.
$$
Note that the abbreviated names are not the official ISIC names. The decision which of the 10 ISIC sectors to model in detail depends on the country context. For Germany, we decided to model the following sectors in detail:

$$
\begin{align}
\text{VAIndustry} & = \mathcal{f}(\text{ConsHH}, \text{ConsGov}, \text{CapForm}, \text{PriceOil}, \text{PriceETS}), \\
\text{VARetail} & = \mathcal{f}(\text{ConsHH}, \text{ConsGov}, \text{CapForm}), \\
\text{VARealEstate} & = \mathcal{f}(\text{ConsHH}, \text{ConsGov}, \text{CapForm}, \text{HousePriceIndex}), \\
\text{VAService} & = \mathcal{f}(\text{ConsHH}, \text{ConsGov}), \\
\text{VAGov} & = \mathcal{f}(\text{ConsHH}, \text{ConsGov}), \\
\end{align}
$$
where $\mathcal{f}$ represents some function of the data, which does not have to be the same across modules, $\text{ConsHH}$ is household consumption, $\text{ConsGov}$ is government consumption, $\text{CapForm}$ is gross fixed capital formation, $\text{PriceOil}$ is the average crude Brent oil price in EUR, $\text{PriceETS}$ is the average annual EU ETS price, and $\text{HousePriceIndex}$ is a house price index. We also tried to include labour costs for each of the sectors but the data is not available for most years.

The other sectors ($\text{VAAgriculture}, \text{VAConstruction}, \text{VAInformationm}, \text{VAFinance}, \text{VAOther}$) are left unmodelled and either need to be provided exogenously or forecasted by some other means, such as simple AR models, when using the model to forecast. We also leave $\text{Taxes}$ and $\text{Subsidies}$ unmodelled. To complete the supply side, we model $\text{Imports}$ as a function of the real effective exchange rate (REER).

$$
\begin{align}
\text{Imports} & = \mathcal{f}(\text{REER}) \\
\end{align}.
$$
The demand side is modelled in a similar way. We start with the decomposition of $\text{GDPExpenditure}$.

$$
\begin{align}
\text{GDPExpenditure} & = \text{ConsHH} + \text{ConsGov} + \text{CapForm} + \text{DInventories} + \text{Exports} - \text{Imports}, \\
\end{align}
$$
where $\text{DInventories}$ is the change in inventories and valuables (vairables P.52 and P.53 in Eurostat) and $\text{Exports}$ represents the country's total exports.

We take government consumption as exogenous and model household consumption as a function of disposable income, the consumer price index, financial wealth, house wealth, and land wealth:

$$
\begin{align}
\text{ConsHH} & = \mathcal{f}(\text{IncomeHH}, \text{HCPI}, \text{FinWealthHH}, \text{HouseWealthHH}, \text{LandWealthHH}). \\
\end{align}
$$
Gross fixed capital formation is decomposed into its constituent parts, of which we model household capital formation in more detail.

$$
\begin{align}
\text{CapForm} = \text{CapFormHH} + \text{CapFormFirm} + \text{CapFormFinFirm} + \text{CapFormGov}, \\
\text{CapFormHH} = \mathcal{f}(\text{IncomeHH}, \text{HCPI}, \text{HousePriceIndex}, \text{BuildingPermits}). \\
\end{align}
$$
Government gross fixed capital formation ($\text{CapFormGov}$) is again left unmodelled. Household gross fixed capital formation consists of dwellings to a large degree, so we include residential building permits measured in square meters of useful fllor area as an explanatory variable. Currently, financial and non-financial firms' capital formation ($\text{CapFormFinFirm}$ and $\text{CapFormFirm}$) are not modelled. Ideally, we would like to have some measure of cash flow or surplus to model these variables but they are not readily available in the Eurostat database.

Like Imports, Exports are modelled as a function of the real effective exchange rate (REER):

$$
\begin{align}
\text{Exports} & = \mathcal{f}(\text{REER}) \\
\end{align}.
$$
Finally, we follow the approach in NAM to close the model by determining $\text{DInventories}$ as a residual term that equates supply and demand. That is,

$$
\begin{align}
\text{DInventories} & = \text{Supply} - \text{ConsHH} - \text{ConsGov} - \text{CapForm} - \text{Exports}. \\
\end{align}
$$
We can later use this as a diagnostic of model fit.

# Model Specification

We now need to translate the model into a specification that can be used by the `run_model` function. This is done as a tibble with three columns, which specify the type of equation (d for definition, n for endogenous), the dependent variable, and the independent variables. For endogenous equations, the package searches over several functional forms and specifications.

```{r}
spec <- tibble(type = c("d", "d"), dependent = c("Supply", "Demand"), independent = c("GDPOutput + Imports", "GDPExpenditure + Imports")) %>% 
  add_row(type = "d", dependent = "GDPOutput", independent = "VA + Taxes - Subsidies") %>%
  add_row(type = "d", dependent = "VA", independent = "VAAgriculture + VAIndustry + VAConstruction + VARetail + VAInformation + VAFinance + VARealEstate + VAService + VAGov + VAOther") %>% 
  add_row(type = "n", dependent = "VAIndustry", independent = "ConsHH + ConsGov + CapForm") %>% # + PriceOil + PriceETS") %>%
  add_row(type = "n", dependent = "VARetail", independent = "ConsHH + ConsGov + CapForm") %>%
  add_row(type = "n", dependent = "VARealEstate", independent = "ConsHH + ConsGov + CapForm + HousePriceIndex") %>% 
  add_row(type = "n", dependent = "VAService", independent = "ConsHH + ConsGov") %>%
  add_row(type = "n", dependent = "VAGov", independent = "ConsHH + ConsGov") %>% 
  add_row(type = "n", dependent = "Imports", independent = "REER") %>% 
  add_row(type = "d", dependent = "GDPExpenditure", independent = "ConsHH + ConsGov + CapForm + DInventories + Exports - Imports") %>% 
  add_row(type = "d", dependent = "DInventories", independent = "Supply - ConsHH - ConsGov - CapForm - Exports") %>%
  add_row(type = "n", dependent = "ConsHH", independent = "IncomeHH + HCPI + FinWealthHH + HouseWealthHH + LandWealthHH") %>% 
  add_row(type = "d", dependent = "CapForm", independent = "CapFormHH + CapFormFirm + CapFormFinFirm + CapFormGov") %>% 
  add_row(type = "n", dependent = "CapFormHH", independent = "IncomeHH + HCPI + HousePriceIndex + BuildingPermits") %>% 
  add_row(type = "n", dependent = "Exports", independent = "REER")
```

# Dictionary

The dictionary is a tibble that specifies the data sources for the variables in the model. In this example, we only rely on data from Eurostat. The dictionary has to specify the model variable name, more detailed description of the variable, in which database it can be found, the dataset id, and the variable code and column in the dataset. Different datasets have different structures, so further columns can act as filters to select the correct data, such as the data frequency, the unit in which it is measured, the NACE/ISIC code etc. If a filter is not present in a specific dataset, it has to be set to `NA`.

**Note from Moritz**

Changed dictionary structure and combined existing ones
see `small_examples/eurostat_dictionary.R`

```{r}
dict_local <- structure(
  list(
    model_varname = c("PriceETS", "PriceOil", "HCPI"),
    full_name = c(
      "Average Annual EU ETS Price, Nominal",
      "Average Crude Brent Oil Price in USD, Nominal",
      "Harmonised Consumer Price Index All Goods"
    ),
    database = c("local", "local", "local"),
    variable_code = c("PriceETS", "PriceOil", NA),
    var_col = c("na_item", "na_item", NA),
    freq = c(NA, NA, "q"),
    geo = c("DE", "DE", NA),
    n = c(1L, 1L, 2L)
  ),
  row.names = c(NA, -3L),
  class = c("tbl_df", "tbl", "data.frame")
)

dictionary <- dplyr::bind_rows(dict_identities, dict_eurostat, dict_edgar, dict_local)
```

## Adding Data Manually

Some of the variables are not available in the Eurostat database. For these variables, we have to provide the data manually. For example, the average annual EU ETS price and the average crude Brent oil price are not available in the Eurostat database. We can add these variables to the dictionary by setting the database to "local" and providing the data in a separate dataset.

They are saved in the folder "data_raw".

EU ETS Price is from the [World Bank's Carbon Price Dashboard](https://carbonpricingdashboard.worldbank.org/about#download-data).

```{r}
ets <- readxl::read_xlsx("./small_examples/illustration de/data_raw/wb_carbon_prices.xlsx", sheet = "Compliance_Price",
                         skip = 1) %>% 
  filter(`Name of the initiative` == "EU ETS") %>% 
  select(1, 7:43)
print(unique(ets$`Price rate label`))
print(unique(ets$Metric))
ets <- ets %>% 
  select(-Metric, -`Price rate label`)
ets <- ets %>% 
  pivot_longer(cols = !`Name of the initiative`, names_to = "time", values_to = "values", values_transform = as.numeric,
               values_drop_na = TRUE) %>% 
  mutate(na_item = "PriceETS",
         time = as.Date(paste0(time, "-01-01")),
         geo = "DE") %>% 
  select(-`Name of the initiative`)
```

Oil Prices are from [Our World in Data](https://ourworldindata.org/grapher/crude-oil-prices).

```{r}
oil <- read.csv("./small_examples/illustration de/data_raw/owid_crude_oil_prices.csv") %>% 
  select(3, 4) %>% 
  rename_with(~c("time", "values")) %>% 
  mutate(na_item = "PriceOil",
         time = as.Date(paste0(time, "-01-01")),
         geo = "DE") %>% 
  filter(time >= as.Date("1990-01-01")) # won't have earlier data anyway for VA
```

Both EU ETS and oil prices are in USD (per tonne of CO2 or per cubic meter, respectively), so we need to convert them to EUR.

Conversion to EUR using [Eurostat's Annual Average Exchange Rates](https://doi.org/10.2908/ERT_BIL_EUR_A). This solution is dirty because prior to 1999, these are not exchange rates against the Euro but the ``ECU'', which is a basket of EU currencies. Ideally, would want to use exchange rate against the Deutsche Mark until 1999 (will have to very by country). For now, use Eurostat solution.

```{r}
xrt <- readxl::read_xlsx("./small_examples/illustration de/data_raw/eurostat_usd_exchange_rates.xlsx",
                         sheet = "Sheet 1", skip = 8) %>% 
  filter(TIME == "US dollar") %>% 
  select(-1) %>% 
  pivot_longer(cols = everything(), names_to = "time", values_to = "values", values_transform = as.numeric) %>% 
  mutate(time = as.Date(paste0(time, "-01-01")),
         na_item = "USDEUR",
         geo = "DE")
```

Combine data and convert to EUR.

```{r}
data <- ets %>% 
  bind_rows(oil) %>% 
  bind_rows(xrt) %>% 
  pivot_wider(names_from = "na_item", values_from = "values") %>% 
  mutate(PriceETS = PriceETS / USDEUR,
         PriceOil = PriceOil / USDEUR) %>% 
  # make PriceETS zero before 2005
  mutate(PriceETS = case_when(time < as.Date("2005-01-01") ~ 0,
                              TRUE ~ PriceETS))
# save as local files to be read
data %>% 
  select(-USDEUR) %>% 
  pivot_longer(cols = c("PriceETS", "PriceOil"), names_to = "na_item", values_to = "values") %>% 
  arrange(time) %>% 
  writexl::write_xlsx(path = "./small_examples/illustration de/data_prep/additional_data.xlsx")
```
We save the manually prepared data as `additional_data.xlsx` in the `data_prep` folder.

# Run Model

```{r}
model_result <- run_model(
  specification = spec,
  dictionary = dictionary %>% mutate(geo = "DE"),
  inputdata_directory = "./small_examples/illustration de/data_prep/",
  save_to_disk = "./small_examples/illustration de/data_prep/downloaded_data.xlsx",
  primary_source = "local",
  trend = FALSE,
  saturation.tpval = 0.01,
  gets_selection = FALSE,
  constrain.to.minimum.sample = FALSE,
  plot = FALSE
)
```

```{r}
model_result
```
# Assess Model Fit

The model is closed by choosing $\text{DInventories}$ as a residual term that equates supply and demand. We can compare it to the data for the change in inventories and valuables that Eurostat provides and see whether they are similar. Moreover, our variable should be stationary because trending behaviour is a sign of model misspecification.

```{r}
DInventories_stat <- eurostat::get_eurostat("nama_10_gdp", filters = list(geo = "DE", na_item = "P52", unit = "CP_MEUR")) %>% 
  drop_na()
DValuables_stat <- eurostat::get_eurostat("nama_10_gdp", filters = list(geo = "DE", na_item = "P53", unit = "CP_MEUR")) %>% 
  drop_na()
# combine
DInventories_stat_wide <- DInventories_stat %>% 
  select(-freq, -unit, -na_item, -geo) %>% 
  rename(dinv = values)
DValuables_stat_wide <- DValuables_stat %>%
  select(-freq, -unit, -na_item, -geo) %>% 
  rename(dval = values)
DInvVal_stat_wide <- full_join(DInventories_stat_wide, DValuables_stat_wide, by = "time")
DInvVal_stat_wide <- DInvVal_stat_wide %>% 
  mutate(dinvval_stat = dinv + dval) %>% 
  select(-dinv, -dval)
ggplot(DInvVal_stat_wide) +
  geom_line(aes(x = time, y = dinvval_stat), color = "blue")

DInvVal_model <- model_result$module_collection[[14, "dataset"]][[1]][, c("time", "DInventories.level.hat")] %>% 
  rename(dinvval_model = DInventories.level.hat)
DInvVal_comp <- full_join(DInvVal_stat_wide, DInvVal_model, by = "time") %>% 
  pivot_longer(cols = c("dinvval_stat", "dinvval_model"), names_to = "source", values_to = "dinvval")

ggplot(DInvVal_comp) +
  geom_line(aes(x = time, y = dinvval, color = source))
```
We have some outlying periods. At least we cannot see trending behaviour of the model variable. Apart from the outliers, the model value is close to the value provided by Eurostat.

# Forecasting

```{r}
model_forecast <- forecast_model(model_result, n.ahead = 5, exog_fill_method = "auto")
model_forecast

model_forecast_ar <- forecast_model(model_result, n.ahead = 5, exog_fill_method = "AR")
model_forecast_last <- forecast_model(model_result, n.ahead = 5, exog_fill_method = "last")
```

<!-- Subsidies are exploding, looks like its AR model is not working well. Get errors when trying to specify a different `exog_fill_method`. -->

<!-- # Converting the Model to Quarterly Data -->


Due to data availability, we had to make some changes to the specification.

```{r}
spec <- tibble(type = c("d", "d"), dependent = c("Supply", "Demand"), independent = c("GDPOutput + Imports", "GDPExpenditure + Imports")) %>% 
  add_row(type = "d", dependent = "GDPOutput", independent = "VA + Taxes - Subsidies") %>%
  add_row(type = "d", dependent = "VA", independent = "VAAgriculture + VAIndustry + VAConstruction + VARetail + VAInformation + VAFinance + VARealEstate + VAService + VAGov + VAOther") %>% 
  add_row(type = "n", dependent = "VAIndustry", independent = "ConsHH + ConsGov + CapForm") %>% # + PriceOil + PriceETS") %>%
  add_row(type = "n", dependent = "VARetail", independent = "ConsHH + ConsGov + CapForm") %>%
  add_row(type = "n", dependent = "VARealEstate", independent = "ConsHH + ConsGov + CapForm + HousePriceIndex") %>% 
  add_row(type = "n", dependent = "VAService", independent = "ConsHH + ConsGov") %>%
  add_row(type = "n", dependent = "VAGov", independent = "ConsHH + ConsGov") %>% 
  add_row(type = "n", dependent = "Imports", independent = "REER") %>% 
  add_row(type = "d", dependent = "GDPExpenditure", independent = "ConsHH + ConsGov + CapForm + DInventories + Exports - Imports") %>% 
  add_row(type = "d", dependent = "DInventories", independent = "Supply - ConsHH - ConsGov - CapForm - Exports") %>%
  add_row(type = "n", dependent = "ConsHH", independent = "IncomeHH + HCPI + FinWealthHH") %>% 
  add_row(type = "d", dependent = "CapForm", independent = "CapFormHH + CapFormFirm + CapFormFinFirm + CapFormGov") %>% 
  add_row(type = "n", dependent = "CapFormHH", independent = "IncomeHH + HCPI + HousePriceIndex + BuildingPermits") %>% 
  add_row(type = "n", dependent = "Exports", independent = "REER")
```



# Moritz part

<!-- ```{r} -->
<!-- moritz_dict <- read_csv("small_examples/illustration de/moritz_dict.csv") -->
<!-- dictionary <- bind_rows(dictionary, moritz_dict %>% filter(!model_varname %in% unique(dictionary$model_varname))) -->
<!-- ``` -->


```{r}
# potential further variables to add: 
# ElectrCons

spec_moritz <- dplyr::tibble(
  type = c(
    "n",
    "n",
    "n",
    "n",
    "n",
    "n",
    "n"
  ),
  dependent = c(
    "EmiCO2Industry",
    "EmiCH4Livestock",
    "Flights",
    "EmiCO2Aviation",
    "RoadFreight",
    "EmiCO2Road",
    "EmiCO2Residential"
  ),
  independent = c(
    "VAIndustry",
    "Subsidies + Slaughter",
    "ConsHH + HICP_AviaInt",
    "Flights + ConsHH",
    "ConsHH + HICP_Diesel + HICP_Petrol + Taxes",
    "RoadFreight + ConsHH + Taxes + HICP_Diesel + HICP_Petrol",
    "ConsHH + HICP_Electricity + FinConsExpHH"
  )
)
```


```{r}
spec <- bind_rows(spec, spec_moritz)
```




```{r}
model_result <- run_model(
  specification = spec,
  dictionary = dictionary %>% mutate(geo = "DE"),
  inputdata_directory = "./small_examples/illustration de/data_prep_quarterly/",
  save_to_disk = "./small_examples/illustration de/data_prep_quarterly/trial_moritz.xlsx",
  primary_source = "local",
  trend = FALSE,
  saturation.tpval = 0.01,
  gets_selection = FALSE,
  constrain.to.minimum.sample = FALSE,
  plot = FALSE
)
```

```{r}
model_result
```

Assess model fit

**Note from Moritz**
- Issues with Flights 
- Issues with CO2 Residential

Both potentially data issues


```{r}
DInventories_stat <- eurostat::get_eurostat("namq_10_gdp", filters = list(geo = "DE", na_item = "P52", unit = "CP_MEUR", s_adj = "NSA")) %>% 
  drop_na()
DValuables_stat <- eurostat::get_eurostat("namq_10_gdp", filters = list(geo = "DE", na_item = "P53", unit = "CP_MEUR", s_adj = "NSA")) %>% 
  drop_na()
# combine
DInventories_stat_wide <- DInventories_stat %>% 
  select(-freq, -unit, -na_item, -geo) %>% 
  rename(dinv = values)
DValuables_stat_wide <- DValuables_stat %>%
  select(-freq, -unit, -na_item, -geo) %>% 
  rename(dval = values)
DInvVal_stat_wide <- full_join(DInventories_stat_wide, DValuables_stat_wide, by = "time")
DInvVal_stat_wide <- DInvVal_stat_wide %>% 
  mutate(dinvval_stat = dinv + dval) %>% 
  select(-dinv, -dval)
ggplot(DInvVal_stat_wide) +
  geom_line(aes(x = time, y = dinvval_stat), color = "blue")

DInvVal_model <- model_result$module_collection[[21, "dataset"]][[1]][, c("time", "DInventories.level.hat")] %>% 
  rename(dinvval_model = DInventories.level.hat)
DInvVal_comp <- full_join(DInvVal_stat_wide, DInvVal_model, by = "time") %>% 
  pivot_longer(cols = c("dinvval_stat", "dinvval_model"), names_to = "source", values_to = "dinvval")

ggplot(DInvVal_comp) +
  geom_line(aes(x = time, y = dinvval, color = source))
```
This looks pretty good.


Forecasting

```{r}
model_forecast <- forecast_model(model_result, n.ahead = 12, exog_fill_method = "auto")
model_forecast2 <- forecast_model(model_result, n.ahead = 12, exog_fill_method = "AR")
model_forecast3 <- forecast_model(model_result, n.ahead = 12, exog_fill_method = "last")
model_forecast
```
Error (no error for "auto" if remove HCIP from the equations).

# Adapting Quarterly Model to Austria

**Note from Moritz**: Not run for Austria yet!


First, remove HCPI from specification b/c was created manually for Germany.

```{r}
spec <- tibble(type = c("d", "d"), dependent = c("Supply", "Demand"), independent = c("GDPOutput + Imports", "GDPExpenditure + Imports")) %>% 
  add_row(type = "d", dependent = "GDPOutput", independent = "VA + Taxes - Subsidies") %>%
  add_row(type = "d", dependent = "VA", independent = "VAAgriculture + VAIndustry + VAConstruction + VARetail + VAInformation + VAFinance + VARealEstate + VAService + VAGov + VAOther") %>% 
  add_row(type = "n", dependent = "VAIndustry", independent = "ConsHH + ConsGov + CapForm") %>% # + PriceOil + PriceETS") %>%
  add_row(type = "n", dependent = "VARetail", independent = "ConsHH + ConsGov + CapForm") %>%
  add_row(type = "n", dependent = "VARealEstate", independent = "ConsHH + ConsGov + CapForm + HousePriceIndex") %>% 
  add_row(type = "n", dependent = "VAService", independent = "ConsHH + ConsGov") %>%
  add_row(type = "n", dependent = "VAGov", independent = "ConsHH + ConsGov") %>% 
  add_row(type = "n", dependent = "Imports", independent = "REER") %>% 
  add_row(type = "d", dependent = "GDPExpenditure", independent = "ConsHH + ConsGov + CapForm + DInventories + Exports - Imports") %>% 
  add_row(type = "d", dependent = "DInventories", independent = "Supply - ConsHH - ConsGov - CapForm - Exports") %>%
  add_row(type = "n", dependent = "ConsHH", independent = "IncomeHH + FinWealthHH") %>% 
  add_row(type = "d", dependent = "CapForm", independent = "CapFormHH + CapFormFirm + CapFormFinFirm + CapFormGov") %>% 
  add_row(type = "n", dependent = "CapFormHH", independent = "IncomeHH + HousePriceIndex + BuildingPermits") %>% 
  add_row(type = "n", dependent = "Exports", independent = "REER")
```

Adjust dictionary to replace "DE" with "AT".

```{r}
dictionary_AT <- dictionary %>% 
  mutate(geo = case_when(geo == "DE" ~ "AT",
                         is.na(geo) ~ NA,
                         TRUE ~ "problem"))
unique(dictionary_AT$geo) # no "problem"
```

```{r}
model_result <- run_model(
  specification = spec,
  dictionary = dictionary_AT,
  inputdata_directory = "./small_examples/illustration de/data_prep_quarterly/",
  save_to_disk = NULL,
  primary_source = "local",
  trend = FALSE,
  saturation.tpval = 0.01,
  gets_selection = FALSE,
  constrain.to.minimum.sample = FALSE,
  plot = FALSE
)
```
```{r}
model_result
```

